---
title: ""
output: html_document

params:
  samplename: 
    value: x
  PeaksUniq:
    value: x
  PeaksFracMM:
    value: x
  OutDIR: 
    value: x
  ntmerge: 
    value: x
  readdepth:
    value: x
  species:
    value: x
  Condense: FALSE
  JoinJunc: TRUE
  calcMAPQ: FALSE
  calcALTLOC: FALSE
  RunMAnorm: FALSE
  DEmethod: 
    value: x
  PeakIdnt: 
    value: x
  AnnoFiles: 
    value: x
  AnnoScript:
    value: x
  OutDIR2:
    value: x
  peak_in:
    value: "/Volumes/data/iCLIP/marco/inprogress/peaks_KO_fCLIP.txt"


---
#update params
peak_in - _peakjunction.txt
peak_annotation - _peakannotation.txt
ncRNA_annotation - ncRNA_Annotations.txt
peak_junction_annotation - input from peakannotatation_junctions.txt
peak_mapq - peakannotation_mapqscore.txt
out_dir - /Volumes/data/iCLIP/confirm/

##TODO determine what is actually needed from this list
```{r echo=F, message=FALSE, warning=FALSE}
#Load libraries
source(file.path(params$AnnoScript))
library(rmarkdown)
library(stringr)
library(rtracklayer)
library(VariantAnnotation)
library(rmarkdown)
library(ggplot2)
library("viridis")
library(edgeR)
library('GenomicFeatures')
library('rtracklayer')
library(matrixStats)
library(plyr)
library(tidyr)
library(fitdistrplus)
library(stringr)
library(data.table)
library(reshape)
library(stringi)
library(BSgenome)
library(plotly)
library(tidyr)
library(GenomicRanges)
library(RColorBrewer)
library('gplots')
library(ggpubr)
library(circlize)
library('regioneR')
library(GenomicAlignments)

```


# Identification of CLIP peaks: `r toString(params$samplename)`    

**Select CLIP peaks**

Identify peaks using bedtools merge on All reads (unique and Multimapping) and count number of reads that overlap with the identified peaks.
  
Peaks with > `r toString(params$readdepth)` (unique + Multi-Mapped:fraction) reads were assessed.  

#remove - added to 07_peak_annotation - remove this
<!-- Peaksdata2 = read.csv(params$peak_in) -->

<!-- #read in peaks file, with annotation info (generated from 07_peak_annotation.R) -->
<!-- Peaksdata2_anno = read.csv(params$peak_annotation) -->
<!-- Peaksdata2_anno = Peaksdata2_anno[,c('chr','start','end','strand')] -->

<!-- ###fix variable swapping -->
<!-- Peaksdata2_annox = Peaksdata2_anno -->

<!-- #merge peak junction and peak annotation information -->
<!-- Peaksdata2_anno = merge(Peaksdata2, -->
<!--                         Peaksdata2_anno[,!colnames(Peaksdata2_anno)%in%c('chr','start','end','strand')], -->
<!--                         by='ID') -->

###phil moved to 07_peak_annotation.R - remove this
<!-- if (params$JoinJunc==TRUE) { -->

<!--   ###recreate original code (line 226) -->
<!--   #Junc_peaks=unique(c(Junc_PL_merged$ID_Peaks1,Junc_PL_merged$ID_Peaks2)) -->
<!--   Junc_peaks = subset(Peaksdata2,TBD = "TBD") -->

<!--   #select peaks with junction -->
<!--   Peaksdata2_anno_trns_exon=( Peaksdata2_anno[Peaksdata2_anno$ID%in%Junc_peaks,]) -->

<!--   #create new df -->
<!--   CollapsedOut=as.data.frame(matrix(nrow = (1),ncol = ncol(Peaksdata2_anno_trns_exon))) -->
<!--   colnames(CollapsedOut)=colnames(Peaksdata2_anno_trns_exon) -->
<!--   CollapsedOut$IDmerge=NA -->

<!--   ###recreate original code (174) -->
<!--   #PGene_TBL2=(matrix(nrow=nrow(PGene_TBL_unique),ncol=ncol(PGene_TBL_unique)+4)) -->
<!--   PGene_TBL2 = subset(Peaksdata2,TBD = "TBD") -->

<!--   #for each unique peak -->
<!--   for (x in 1:nrow(PGene_TBL2)) { -->

<!--     #select row -->
<!--     Trnsc=PGene_TBL2[x,] -->

<!--     #split ID -->
<!--     TrnscUL=unlist(unique(str_split(Trnsc$ID_comb,pattern = ","))) -->

<!--     #create df of id annotation information -->
<!--     d2=Peaksdata2_anno_trns_exon[Peaksdata2_anno_trns_exon$ID%in%TrnscUL,] -->

<!--     #if the line isn't in the annotation file -->
<!--     ###phil - we should prob do some error handling here; we shouldn't have instances -->
<!--     #where this is true, unless there are no peaks? and then this whole thing should stop, right?  -->
<!--     if (nrow(d2)==0) { -->
<!--       next -->
<!--     } else{ -->
<!--       print("ERROR") -->
<!--     } -->

<!--     #Positive strand -->
<!--     ###fix variables -->
<!--     if (unique(d2$strand)=="+") { -->
<!--       d5=d2[d2$start%in%min(d2$start),]  -->
<!--       dmax=d2[d2$Counts_fracMM%in%max(d2$Counts_fracMM),] -->

<!--       ###phil need error  handling here -->
<!--       if (nrow(dmax)>1) { -->
<!--         dmax=dmax[dmax$start%in%min(dmax$start),] -->
<!--       } else{ -->
<!--         print ("TBD") -->
<!--       } -->
<!--     #negative strand -->
<!--     } else if (unique(d2$strand)=="-") { -->
<!--       d5=d2[d2$start%in%max(d2$start),] -->
<!--       dmax=d2[d2$Counts_fracMM%in%max(d2$Counts_fracMM),] -->

<!--       ###phil need error handling here -->
<!--       if (nrow(dmax)>1) { -->
<!--         dmax=dmax[dmax$start%in%max(dmax$start),] -->
<!--       } else{ -->
<!--         print("TBD") -->
<!--       } -->
<!--     } -->

<!--     ### collapse all columns  -->
<!--     d3 = (apply(d2 ,2, function(x){paste(unique(x[!is.na(x)]),collapse = ',')})) -->
<!--     d3[d3==""]<-NA -->

<!--     cols=c('Counts_Unique','Counts_fracMM','Length') -->
<!--     d3=as.data.frame(t(d3)) -->
<!--     d3[1,cols] = t(as.data.frame(colSums(d2[,cols])))    -->
<!--     d3[,cols] = as.numeric(d3[,cols]) -->
<!--     d3$IDmerge=d3$ID -->

<!--     ## Select summary annotation based on Max(dmax) expression peak or 5'(d5) peak    -->
<!--     danno=dmax # d5 dmax -->
<!--     cols_AnnotSelect=c('Same_Comb_type_exon', 'Same_Comb_type_ncRNA', -->
<!--                        'Oppo_Comb_type_exon','Oppo_Comb_type_ncRNA','Comb_type_exon_Oppo') -->
<!--     d3[,cols_AnnotSelect]= (danno[,cols_AnnotSelect]) -->

<!--     # Select ID for 5' most read or max counts -->
<!--     d3$start=d5$start -->
<!--     d3$end=d5$end -->
<!--     d3$ID=paste0(dmax$chr,":",dmax$start,"-",dmax$end)    -->

<!--     ## if count < readdepth skip -->
<!--     if (d3$Counts_fracMM<params$readdepth) { -->
<!--       next -->
<!--     } -->

<!--     CollapsedOut=rbind(CollapsedOut[,colnames(CollapsedOut)],d3[1,colnames(CollapsedOut)]) -->
<!--   } -->

<!--   #remove rows without id -->
<!--   CollapsedOut = complete.cases(CollapsedOut[,"ID"]) -->

<!--   ###fix variable we dont want to overwrite the original -->
<!--   #subset for all non-junction peaks -->
<!--   Peaksdata2_anno$IDmerge=NA -->
<!--   Peaksdata2_anno=subset(Peaksdata2_anno, !(ID%in%Junc_peaks)) -->

<!--   #merge non-junction peaks (Peaksdata2_anno) with junction peaks (CollapsedOut) -->
<!--   Peaksdata2_anno=(rbind(Peaksdata2_anno,CollapsedOut)) -->

<!--   #### Re filter reads after combing counts of spliced reads -->
<!--   Peaksdata2_anno=Peaksdata2_anno[Peaksdata2_anno$Counts_fracMM>=params$readdepth,] -->

<!-- } else if (params$JoinJunc==FALSE) { -->

<!--   ###phil need to fill else statement -->
<!--   # collapse exon -->
<!--   if (params$Condense==TRUE) { -->
<!--     Peaksdata2_anno_trns_exon = subset(Peaksdata2_anno, !(Same_feature == "") & -->
<!--                                          Comb_type_exon_Oppo == 'protein_coding: exon') -->
<!--     #create list -->
<!--     trns=Peaksdata2_anno_trns_exon$Same_ensembl_gene_id -->

<!--     ###fix variable naming -->
<!--     trns=trns[grep(",",trns)] -->
<!--     trns=c(Peaksdata2_anno_trns_exon$Same_ensembl_gene_id,unlist(strsplit(trns,","))) -->

<!--     #remove dups -->
<!--     dupGeneName=unique(trns[duplicated(trns)]) -->

<!--     #create df -->
<!--     CollapsedOut = as.data.frame(matrix( nrow = 1, -->
<!--                           ncol = ncol(Peaksdata2_anno_trns_exon)+1)) -->
<!--     colnames(CollapsedOut)=c(colnames(Peaksdata2_anno_trns_exon),'IDmerge') -->

<!--     #for each unique val -->
<!--     for (x in 1:length(dupGeneName)) { -->
<!--       d1=dupGeneName[x] -->
<!--       d2=Peaksdata2_anno_trns_exon[grep(d1,Peaksdata2_anno_trns_exon$Same_ensembl_gene_id),] -->
<!--       d2ID=paste0(d2$chr[1],":",min(d2$start),"-",max(d2$end)) -->

<!--       #positive strand -->
<!--       if (unique(d2$strand)=="+") { -->
<!--         d3=d2[d2$start%in%min(d2$start),] -->
<!--         #negative strand -->
<!--       } else if (unique(d2$strand)=="-") { -->
<!--         d3=d2[d2$start%in%max(d2$start),] -->
<!--       } -->

<!--       d3[,'start']=min(d2$start) -->
<!--       d3[,'end']=max(d2$end) -->
<!--       d3$IDmerge=paste(d2$ID,collapse = ",") -->

<!--       trns=trns[grep(",",d2$Same_ensembl_gene_id)] -->
<!--       d3$Same_ensembl_gene_id = paste0(unique(c(d2$Same_ensembl_gene_id,unlist(strsplit(trns,",")))), -->
<!--                                        collapse = ",") -->
<!--       trns=trns[grep(",",d2$Same_gene_name_comb)] -->
<!--       d3$Same_gene_name_comb=paste0(unique(c(d2$Same_gene_name_comb,unlist(strsplit(trns,",")))), -->
<!--                                     collapse = ",") -->
<!--       trns=trns[grep(",",d2$`Opposite Strand: Host_gene_ensembl_id`)] -->
<!--       d3$Oppo_ensembl_gene_id=paste0(unique(c(d2$Oppo_ensembl_gene_id,unlist(strsplit(trns,",")))), -->
<!--                                      collapse = ",") -->
<!--       trns=trns[grep(",",d2$Oppo_gene_name_comb)] -->
<!--       d3$Oppo_gene_name_comb=paste0(unique(c(d2$Oppo_gene_name_comb,unlist(strsplit(trns,",")))), -->
<!--                                     collapse = ",") -->
<!--       CollapsedOut=rbind(CollapsedOut,d3) -->
<!--     } -->

<!--     #remove rownames, col -->
<!--     rownames(CollapsedOut)=NULL -->
<!--     CollapsedOut=CollapsedOut[-1,] -->
<!--     CollapsedOutID= unique(unlist(strsplit(CollapsedOut$IDmerge,","))) -->

<!--     ###fix we dont want to overwrite original df -->
<!--     Peaksdata2_anno$IDmerge=NA -->
<!--     Peaksdata2_anno=Peaksdata2_anno[Peaksdata2_anno$ID%in%CollapsedOutID==F,] -->
<!--     Peaksdata2_anno=(rbind(Peaksdata2_anno,CollapsedOut)) -->
<!--   } -->
<!-- } -->


#Generate Peak Counts graphics
```{r ,fig.align='center',echo=F,warning=F,eval=T,include=T}
###fix variable
Peaksdata2_anno = read.csv(params$peak_annotated)

if (params$PeakIdnt=='Unique'){
  x = ggplot(Peaksdata2_anno, aes(x=Counts_Unique)) +
    geom_histogram(bins = 30) +
    scale_x_continuous(trans = "log2") + 
    theme_classic()+ylab("# of peaks") + 
    xlab("Peak Counts (unique)") + 
    ggtitle("Distribution of peak counts")
  ggplotly(x,tooltip = c("x", "y"))
} else if (params$PeakIdnt=='all'){
  x = ggplot(Peaksdata2_anno, aes(x=Counts_fracMM)) +
    geom_histogram(bins = 30) +
    scale_x_continuous(trans = "log2") + 
    theme_classic()+ylab("# of peaks") + 
    xlab("Peak Counts (Unique + FracMM)") + 
    ggtitle("Distribution of peak counts")
  ggplotly(x,tooltip = c("x", "y"))
}
```

###phil we should remove any text that you don't want to include for read-ability
<br/>    
  <br/>    
  
  
  ## Identify CLIP peak Gene Location  
  
  ### Identify if CLIP peak overlaps with Intron or Exonic region   
  
  <br>  
  
  <!-- Intron coordinates were calculated from GTF file. -->
  
  <!-- A second column was added to idenify if the peak also overlapped with the 5'UTR 3'UTR or CDS (Column: Featrue 2) -->
  
  Protein Coding Genes were taken from `r toString(refGTF)` GTF file.     

Peaks were annotated with overlapping gene/transcript  

Peaks were annotated by whether they overlap with Host gene intron/exon region  

<br>   
  
  ### Identify CLIP peak in ncRNA   
  
  
```{r echo=F,results='asis',eval=T}
Classification_ncRNA=read.delim(params$ncRNA_annotation, header=T, sep="\t",stringsAsFactors = F)
kable(Classification_ncRNA[,1:3])
```

<br>  
  
  
  ### Identify peaks in repeat regions   
  
  Annotate all repeat regions/Classes identified in Repeatmasker Annotation file (UCSC Table browser)  
Data was not filtered based on any of the identified Repeats.  
1) LINE/SINE   
2) LTR   
3) DNA   
4) Satellites   
5) Simple Repeats   
6) Low Complexity   
7) Other   
8) Unknown   
<br>
  
#Plot repeat region peaks
```{r echo=F,warning=F, include=T,eval=T,fig.align='center'}
###phil - we should breakdown this calc - not sure what it's showing
p=as.data.frame(((colSums(is.na(Peaksdata2_anno[,grep('Same_Repeat_',colnames(Peaksdata2_anno))])==F)/nrow(Peaksdata2_anno))*100))
p$Repeat_Type=rownames(p)
colnames(p)=c('Frequency','Repeat_Type')
p=p[rownames(p)%in%'Same_Repeat_comb'==F,]
p$Repeat_Type=gsub("Same_Repeat_","",p$Repeat_Type)

ggplot(p) + 
  geom_bar(aes(x=Repeat_Type,y=Frequency),stat="identity")+theme_classic() +
  xlab("") +
  ylab("Frequency of peaks in \nrepeat regions (%)")+ggtitle("Same Strand") +
  theme(plot.title = element_text(hjust = 0.5,
                                  size = 15), 
        axis.title=element_text(size=15),
        axis.text=element_text(size=10),
        legend.text = element_text( size=10)) +
  theme(axis.text.x = element_text(angle = -45))
```

###phil - removed handled in 08_mapq_calculation.R
<!-- write.table(Peaksdata2_anno[,c('chr','start','end','strand','ID')], -->
<!--             file=paste0(params$OutDIR,"/MAPQ/CLIP_",samplename,"_", -->
<!--                         params$PeakIdnt,"Peaks",ntmerge,'_peakDepth', -->
<!--                         params$readdepth,params$NameAdd,"_mapq_IN.txt"),  -->
<!--             sep = "\t", row.names = FALSE, col.names = T, append = F, quote= FALSE,na = "") -->

<!-- if (calcMAPQ==TRUE { -->
<!--   param <- ScanBamParam(what=c("mapq", "flag")) -->
<!--   Bam=readGAlignments(paste0(INbam,samplename,'_Clip_iCountcutadpt_all.unique.NH.mm.ddup.bam'),use.names=T,index='./bam/ddup/Ro/Ro_Clip_iCountcutadpt_all.unique.NH.mm.ddup.bam.bai', param=param) -->
<!--   # colnames(as.data.frame(Bam)) -->
<!--   mcols(Bam)$qname=names(Bam) -->

<!--   glist=function(i){ -->
<!--     PL=i -->
<!--     GRanges(seqnames = as.character(PL[1]), ranges=IRanges(start = as.numeric(PL[2]), end = as.numeric(PL[3])),strand = PL[4]) -->
<!--   } -->
<!--   gout=apply(Peaksdata2_RP[,c('chr','start','end','strand','ID')],1,glist) -->

<!--   mapq=function(i){ -->
<!--     out1=as.data.frame(matrix(nrow=1,ncol=2)); -->
<!--     q=i -->
<!--     s = Bam -->
<!--     xo=as.data.frame(GenomicRanges::findOverlaps(q,s,type = "any",ignore.strand=F)) -->
<!--    sh=as.data.frame(s[xo$subjectHits],row.names = NULL) -->
<!--     mean(sh$mapq,na.rm = T) -->
<!--   } -->
<!--   system.time({outl=mclapply(gout,mapq,mc.cores=3)}  ) -->

<!--   Peaksdata2_RP$Avg_mapq=unlist(outl ) -->
<!--   Peaksdata2_anno=Peaksdata2_RP -->

<!--   write.table(Peaksdata2_RP[,c('ID','Avg_mapq')], -->
<!--               file=paste0(params$OutDIR,"CLIP_", -->
<!--                           params$PeakIdnt,"Peaks", -->
<!--                           ntmerge,'_peakDepth', -->
<!--                           params$readdepth,params$NameAdd,"_mapq.txt"),  -->
<!--               sep = "\t", row.names = FALSE, col.names = T, append = F, quote= FALSE,na = "") -->
<!-- } else if (calcMAPQ==FALSE) { -->
<!--   CLIP_Peaks_mapq=fread(paste0(inMAPQ,"CLIP_Peaks_mapq.txt"),  -->
<!--                         header=T, sep="\t",stringsAsFactors = F,data.table=F) -->
<!--   Peaksdata2_anno= merge(Peaksdata2_anno,CLIP_Peaks_mapq,by="ID",all.x = T) -->
<!-- } -->


<br>   
  <br>   
  
  ### Asigning Clip peak attributes   
  
  Not all Peaks overlap with a single feature so peak assignments were assigned by priority:  
  
  <!-- **ncRNA > Protein coding : Exonic > repeats > Pseudogene > Antisense Feature > Protein Coding : Intronic > lncRNA > no Feature**    -->
  
  **ncRNA > protein_coding: Exonic > Repeat Element > pseudogene > lncRNA: Exonic > Antisense Feature > protein_coding: Intronic > lncRNA: Intronic > no Feature**
  
  <!-- rDNA transcript (BK000964.3) was included in reference genome but not included in peak counts. rDNA will affect multimapping count and will show up in alternative mapping location.   	 -->
  
  All annotations from RNA type, Repeat regions, and Intronic/exonic regions are annotated in the Table.   

<br>  
  <br>  
  
  

## Overview of Ro targets by CLIP peak catagory   
    ```{r , echo=F, include=T, eval=T, fig.align='default', fig.ncol=2, fig.height=3.5, fig.width=7, out.height=200, out.width="50%", fig.show="hold", layout='l-screen', results = FALSE, message=FALSE , warning=F}
###phil we'll need to figure out how these graphs will work since we're running 
    #these as a merge now

###fix variable
#read in peak_junction > pean_annotation > mapq file
###phil 
Peaksdata2_anno = read.csv(params$peak_mapq)
    
if (params$PeakIdnt=='Unique'){
  
  #plot peak counts and width
  x1 = ggplot(Peaksdata2_anno,
              aes(x=Counts_Unique,y=Length,color=Comb_type_exon_Oppo,
                  text=Same_external_gene_name))+geom_point(size=1) + 
    scale_x_continuous(trans = "log2")+scale_y_continuous(trans = "log2") + 
    theme_classic() +
    ylab("Peak Width") + 
    xlab("Peak Counts (unique)") +
    ggtitle("Comparison of peak counts and Peak Width") +
    scale_color_brewer(palette = "Dark2")
  
    x5 = ggplot(Peaksdata2_anno,
                aes(x=Counts_Unique,line=Comb_type_exon_Oppo,color=Comb_type_exon_Oppo)) +
      geom_density()+scale_x_continuous(trans = "log2") + 
      theme_classic()+ylab("Density") + 
      xlab("Peak Counts (unique)")+ggtitle("Distribution of peak counts") +
      labs(color='RNA Type') +
    scale_color_brewer(palette = "Dark2")
    
} else if (params$PeakIdnt=='MultiMap'){
  x1 = ggplot(Peaksdata2_anno,
              aes(x=Counts_MM,y=Length,color=Comb_type_exon_Oppo,
                  text=Same_external_gene_name)) +
    geom_point(size=1) +
    scale_x_continuous(trans = "log2") +
    scale_y_continuous(trans = "log2") + theme_classic() +
    ylab("Peak Width") +
    xlab("Peak Counts (MultiMap)") +
    ggtitle("Comparison of peak counts and Peak Width") +
    scale_color_brewer(palette = "Dark2")
  
  x5 = ggplot(Peaksdata2_anno,aes(x=Counts_Unique,line=Comb_type_exon_Oppo,color=Comb_type_exon_Oppo)) +
    geom_density()+scale_x_continuous(trans = "log2") + 
    theme_classic()+ylab("Density") +
    xlab("Peak Counts (Counts_MM)") +
    ggtitle("Distribution of peak counts") +
    labs(color='RNA Type') +
    scale_color_brewer(palette = "Dark2") 
}else if (params$PeakIdnt=='all'){
  x1 = ggplot(Peaksdata2_anno,
              aes(x=Counts_fracMM,y=Length,color=Comb_type_exon_Oppo,
                  text=Same_external_gene_name)) +
    geom_point(size=1) +
    scale_x_continuous(trans = "log2") +
    scale_y_continuous(trans = "log2") + 
    theme_classic()+
    ylab("Peak Width") +
    xlab("Peak Counts (Unique+ FracMM)") +
    ggtitle("Comparison of peak counts and Peak Width") +
    labs(color='RNA Type')+
    scale_color_brewer(palette = "Dark2")
  
  x5 = ggplot(Peaksdata2_anno,aes(x=Counts_Unique,line=Comb_type_exon_Oppo,color=Comb_type_exon_Oppo)) +
    geom_density() +
    scale_x_continuous(trans = "log2") +
    theme_classic()+ylab("Density") +
    xlab("Peak Counts (Unique+ FracMM)") +
    ggtitle("Distribution of peak counts") +
    labs(color='RNA Type')+
    scale_color_brewer(palette = "Dark2") 
}

x2 = ggplot(Peaksdata2_anno,aes(x=Length)) +
  geom_histogram(bins = 100) +
  scale_x_continuous(trans = "log2") + 
  theme_classic()+ylab("# of peaks") +
  xlab("Peak Width")+ggtitle("Distribution of peak Width")
  
x3 = ggplot(Peaksdata2_anno,
            aes(x=Length,line=Comb_type_exon_Oppo,color=Comb_type_exon_Oppo)) +
  geom_density(size=.5) +
  scale_x_continuous(trans = "log2") +
  theme_classic()+ylab("Density") + 
  xlab("Peak Width")+ggtitle("Distribution of peak Width")+ 
  labs(color='RNA Type') +
  scale_color_brewer(palette = "Dark2") 

x4 = ggplot(Peaksdata2_anno,
            aes(x=Length,line=Comb_type_exon_Oppo,color=Comb_type_exon_Oppo)) +
  geom_freqpoly(bins = 100) +
  scale_x_continuous(trans = "log2") + 
  theme_classic()+ylab("# of peaks") + 
  xlab("Peak Width")+ggtitle("Distribution of peak Width") +
  labs(color='RNA Type') +
  scale_color_brewer(palette = "Dark2") 

###fix need to label each graph, can prob write a function later
x1;x2;x3;x4;x5
```


<br>  
  <br>   

```{r}
###phil a number of the graphs below is using a similar df - included them all here so we can 
#make universal edits, see if any of these can be merged, and prob avoid re-writing cols (p$Same_Comb_type_exon=p$Comb_type_exon_Oppo)
#and just make edits to that col, since this is "p" is a tmp variable 

#version 1
###fix variable names
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
p[is.na(p$Comb_type_exon),'Same_Comb_type_exon']='no Feature'
colnames(p)[colnames(p)%in%'Same_Comb_type_exon']='RNA_Type'
#phil why are we clearing this col?
p$RNA=''

#version 2
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
p=p[p$Same_Comb_type_exon%in%'ncRNA','Same_Comb_type_ncRNA',drop=F]
p$RNA=""

#version 3
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
###phil - this isn't being run since this variable is never set
if (incd_rRNA==FALSE) {
  p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
}
p[is.na(p$Same_Comb_type_exon),'Same_Comb_type_exon']='no Feature'
colnames(p)[colnames(p)%in%'Same_Comb_type_exon']='RNA_Type'
p$RNA=''

#version 4
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
if (incd_rRNA==FALSE) {
  p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
}
p=p[p$Same_Comb_type_exon%in%'ncRNA','Same_Comb_type_ncRNA',drop=F]
p$RNA="" 

#version 5
p=Peaksdata2_anno
colnames(p)[colnames(p)%in%'Comb_type_exon_Oppo']='RNA_Type'
p$RNA=''

#version 6
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
p[p$Same_Comb_type_ncRNA%in%'rRNA','Same_Comb_type_exon']='rRNA'
p[p$Same_Comb_type_ncRNA%in%'yRNA','Same_Comb_type_exon']='yRNA'

#version 7 
p=Peaksdata2_anno
if (incd_rRNA==F) {
  p=subset(p,!(Oppo_Comb_type_ncRNA == 'rRNA'))
}

#version 8
p=Peaksdata2_anno
if (incd_rRNA==F) {
  p=subset(p,!(Oppo_Comb_type_ncRNA == 'rRNA'))
}
p = subset(p,Oppo_Comb_type_exon == 'ncRNA'))
```
  <!-- ##  Peak Attributes    -->
  
  ##  Number of peaks assigned to each catagory  
  
  **Peak counts do not include rRNA peaks**   
  
```{r fig.asp=.5, fig.align='center',fig.height=4, fig.width=8,echo=F,warning=F,eval=T,include=T}
#version 1
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
p[is.na(p$Comb_type_exon),'Same_Comb_type_exon']='no Feature'
colnames(p)[colnames(p)%in%'Same_Comb_type_exon']='RNA_Type'
p$RNA=''

gg=ggplot(p,aes(fill=RNA_Type,x=RNA) ) +
  geom_bar(position="stack",width=.5) +
  theme_classic() +
  ggtitle("Number of peaks by catagory\n(Determined by unique reads only)") +
  scale_fill_brewer(palette = "Dark2") 
ggplotly(gg)
```

<!-- <font size="1">Columns: RNA_type_Classification </font>      -->
  <!-- <br/>      -->
  
  
```{r fig.asp=.5, fig.align='center',fig.height=4, fig.width=8,echo=F,warning=F,eval=T,include=T}
#version 2
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
p=p[p$Same_Comb_type_exon%in%'ncRNA','Same_Comb_type_ncRNA',drop=F]
p$RNA=""
 
if (nrow(p)>0) {
  gg=ggplot(p,aes(fill=Same_Comb_type_ncRNA,x=RNA) ) + 
    geom_bar(width=.5)+theme_classic() +
    ggtitle("Number of peaks by catagory : ncRNA only\n(Determined by unique reads only)") +  labs(fill='ncRNA Type') +
    scale_color_brewer(palette = "Paired") + 
    scale_fill_brewer(palette = "Paired") + 
    blank_theme + 
    coord_polar("y",start=0)
  (gg)
}
```       

<br>  
  <br>   
  <!-- ## Overview of Ro targets by CLIP peak attributes (no rRNA peaks) -->
  
  **Peak counts do include rRNA peaks**   
  
```{r fig.asp=.5, fig.align='center',fig.height=4, fig.width=8,echo=F,warning=F,eval=T,include=T}
#version 3
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
if (incd_rRNA==FALSE) {
  p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
}
p[is.na(p$Same_Comb_type_exon),'Same_Comb_type_exon']='no Feature'
colnames(p)[colnames(p)%in%'Same_Comb_type_exon']='RNA_Type'
p$RNA=''

gg = ggplot(p,aes(fill=RNA_Type,x=RNA) ) +
  geom_bar(position="stack",width=.5) +
  theme_classic() +
  ggtitle("BioType - Counted by catagory\n(Each Clip Peak only Counted Once)") +
  scale_fill_brewer(palette = "Dark2") 
ggplotly(gg)

```

<!-- <font size="1">Columns: RNA_type_Classification </font>      -->
  <!-- <br/>      -->
  
```{r fig.asp=.5, fig.align='center',fig.height=4, fig.width=8,echo=F,warning=F,eval=T,include=T}
#version 4
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
if (incd_rRNA==FALSE) {
  p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
}
p=subset(p,Same_Comb_type_exon == c("ncRNA","Same_Comb_type_ncRNA"))
p$RNA="" 

###phil we need error handling here
if (nrow(p)>0) {
  gg=ggplot(p,aes(fill=Same_Comb_type_ncRNA,x=RNA) ) +
    geom_bar(width=.5)+theme_classic()+ggtitle("ncRNA only: # of peaks per catagory") + 
    labs(fill='RNA Type') +
    scale_color_brewer(palette = "Paired") +
    scale_fill_brewer(palette = "Paired") + 
    blank_theme + 
    coord_polar("y",start=0)
  (gg)
}
```

<!-- ## Calculate average MAPQ for each peak    -->
  
  <!-- We can plot the average Mapping Quality (MAPQ) of each peak to identify the confidence of read mapping. We see that repeat regions have generally lower mapping quality.     -->
  
  <!-- <br>   -->
```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,incude=T}
### fix variable
#version 5
p=Peaksdata2_anno
colnames(p)[colnames(p)%in%'Comb_type_exon_Oppo']='RNA_Type'
p$RNA=''

gg=ggplot(p,aes(x=RNA_Type,y=Avg_mapq,fill=RNA_Type) ) +
  geom_violin()+theme_classic() +
  geom_jitter(height = 0, width = 0.1,size=1) +
  ggtitle('Average MAPQ for Ro-Clip peak\nby Feature')+ylab("Avg_mapq - Ro-Clip") +
  xlab("") +
  theme(plot.title = element_text(hjust = 0.5,
                                  size = 25),
        axis.title=element_text(size=20),
        axis.text=element_text(size=15)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = -45))
gg

### fix variable
p=Peaksdata2_anno

#select repeat elements
p=p[p$Comb_type_exon_Oppo%in%'Repeat Element',]

###phil add comment
p=p[,c('ID','Avg_mapq',colnames(p)[grep('Same_Repeat_',colnames(p))])]

###phil add comment, i'm not sure what we're filtering
p2=p[,colnames(p)[grep('Same_Repeat_',colnames(p))]]
p2[,colnames(p2)[grep('Same_Repeat_',colnames(p2))]]=as.numeric(is.na(p2[,colnames(p2)[grep('Same_Repeat_',colnames(p2))]])==F)
p2[p2[,colnames(p2)[grep('Same_Repeat_',colnames(p2))]]==0]=NA

###phil we're going to need an IF here - in the instance we don't do mapq then 
#we need to skip this whole section i think?
p2=(p2*p$Avg_mapq)
p2=melt.data.frame(p2,id.vars = NULL)
p2$variable=gsub("Same_Repeat_","",p2$variable)

gg = ggplot(p2,aes(x=variable,y=value,fill=variable) ) +
  geom_violin()+theme_classic() +
  geom_jitter( width = 0.1,size=1) +
  ggtitle('Same Strand: Repeat Element\nAverage MAPQ for Ro-Clip peak') +
  ylab("Avg_mapq - Ro-Clip")+xlab("")+
  theme(plot.title = element_text(hjust = 0.5,size = 25),axis.title=element_text(size=20),
        axis.text=element_text(size=15)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = -45)) + 
  scale_fill_brewer(palette = "Paired")
gg

###fix variable
p=Peaksdata2_anno
p=p[p$Comb_type_exon_Oppo%in%'Repeat Element',]
subset(p, Comb_type_exon_Oppo == 'Repeat Element')
p=p[,c('ID','Avg_mapq',colnames(p)[grep('Oppo_Repeat_',colnames(p))])]
p2=p[,colnames(p)[grep('Oppo_Repeat_',colnames(p))]]
p2[,colnames(p2)[grep('Oppo_Repeat_',colnames(p2))]]=as.numeric(is.na(p2[,colnames(p2)[grep('Oppo_Repeat_',colnames(p2))]])==F)

p2[p2[,colnames(p2)[grep('Oppo_Repeat_',colnames(p2))]]==0]=NA
p2=(p2*p$Avg_mapq)

p2=melt(p2,id.vars = NULL)
p2$variable=gsub("Oppo_Repeat_","",p2$variable)

gg = ggplot(p2,aes(x=variable,y=value,fill=variable) ) +
  geom_violin()+theme_classic() +
  geom_jitter( width = 0.1,size=1) +
  ggtitle('Opposite strand feature: Repeat Element\nAverage MAPQ for Ro-Clip peak') +
  ylab("Avg_mapq - Ro-Clip")+xlab("") +
  theme(plot.title = element_text(hjust = 0.5,size = 25),
        axis.title=element_text(size=20),
        axis.text=element_text(size=15)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = -45))
gg

```

<!-- <br>    -->
  
  <!-- For comparison the average peak MAPQ is ploted for each ncRNA subtype.    -->
  
  <!-- <br>   -->
  
```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,incude=T}
###phil - same as above - if statement for MAPQ
p=Peaksdata2_anno
p=p[p$Comb_type_exon_Oppo%in%'ncRNA',]
if (nrow(p)>0) {
  colnames(p)[colnames(p)%in%'Same_Comb_type_ncRNA']='RNA_Type'
  
  gg = ggplot(p,aes(x=RNA_Type,y=Avg_mapq,fill=RNA_Type) ) +
    geom_violin() +
    theme_classic() +
    geom_jitter( width = 0.1,size=1)+
    ggtitle('Average MAPQ for Ro-Clip peak\nby ncRNA Type') + 
    ylab("Average MAPQ - Ro-Clip")+xlab("")+
    theme(plot.title = element_text(hjust = 0.5,
                                    size = 25),
          axis.title=element_text(size=20),
          axis.text=element_text(size=15)) +
    theme(legend.position = "none") +
    theme(axis.text.x = element_text(angle = -45)) +
    scale_fill_brewer(palette = "Paired")
  gg
}
```
<!-- <br>    -->
  <!-- <br>    -->
  
  <br>  
  <br>   
  <br>   
  
  ## Number of reads assigned to each category   
  
  #### Counts for RNA biotype  
  
  <br>   
  
```{r fig.asp=.5, fig.align='center',fig.height=4, fig.width=8,echo=F,warning=F,include=T,eval=T}
# brewer.pal(n = 8, name = "Dark2")

nc_color=c("#1B9E77","#1fb487","#2bdba6" ,
           "#D95F02", "#7570B3" ,"#E7298A", "#66A61E", "#E6AB02", "#A6761D", "#666666")

#version 6
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
p[p$Same_Comb_type_ncRNA%in%'rRNA','Same_Comb_type_exon']='rRNA'
p[p$Same_Comb_type_ncRNA%in%'yRNA','Same_Comb_type_exon']='yRNA'

###phil - we should avoid hardcoding levels in the instance we expand this list later, or a 
#dataset doesnt have one of these... do we need factors?
p$Same_Comb_type_exon = factor(p$Same_Comb_type_exon, 
                               levels = c("ncRNA","rRNA","yRNA", 
                                          "protein_coding: exon", "Repeat Element",
                                          "pseudogene","Antisense Feature",
                                          "protein_coding: Intron","lncRNA",
                                          "no Feature"))

u=unique(p$Same_Comb_type_exon)
pcount=data.frame(u,1:length(u));colnames(pcount)=c('RNA_Type','Counts_All')

###phil - you don't need to NA a col to add it... you can just add the name
#we should only use NA if we are going to have empty rows (in this case i dont
#think that we should?)
#pcount$Counts_Unique=NA
#pcount$Counts_MM=NA
#pcount$Peak_count=NA

for (x in 1:length(u)) {
  pam=p[p$Same_Comb_type_exon%in%u[x],]
  pcount[x,1]=u[x]
  pcount[x,'Counts_Unique']=colSums(pam[,'Counts_Unique',drop=F],na.rm = T)
  pcount[x,'Counts_fracMM']=colSums(pam[,'Counts_fracMM',drop=F],na.rm = T)
  pcount[x,'Peak_count']=nrow(pam)
  
}
###phil why are we adding this empty col again? if you want the x label to be blank
#we can add this with xlab in ggplot
pcount$RNA=""

### fix check MM vs unique? will this work? 
if (params$PeakIdnt=='MultiMap'){
  gg = ggplot(pcount,
              aes(fill=RNA_Type,x=RNA,y=Counts_MM)) +
    geom_bar(stat='identity',position="stack",width=.5) +
    theme_classic() +
    ggtitle("BioType - # of reads (MultiMap) by catagory)") +
    scale_fill_manual(values=nc_color)
  ggplotly(gg)
}

gg = ggplot(pcount,
            aes(fill=RNA_Type,x=RNA,y=Counts_Unique) ) +
  geom_bar(stat='identity',position="stack",width=.5) +
  theme_classic()+ggtitle("BioType - # of reads (unique) by catagory)") +
  scale_fill_manual(values=nc_color)
ggplotly(gg)

gg = ggplot(pcount,aes(fill=RNA_Type,x=RNA,y=Counts_fracMM) ) +
  geom_bar(stat='identity',position="stack",width=.5) +
  theme_classic()+ggtitle("BioType - # of reads (unique + Frac. MM) by catagory)") +
  scale_fill_manual(values=nc_color)
ggplotly(gg)
```
<br>    
  
  #### Counts for ncRNA      
```{r fig.asp=.5, fig.align='center',fig.height=4, fig.width=8,echo=F,warning=F,include=T,eval=T}
#version 6
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
p[p$Same_Comb_type_ncRNA%in%'rRNA','Same_Comb_type_exon']='rRNA'
p[p$Same_Comb_type_ncRNA%in%'yRNA','Same_Comb_type_exon']='yRNA'

###phil - we should avoid hardcoding levels in the instance we expand this list later, or a 
#dataset doesnt have one of these... do we need factors?
p$Same_Comb_type_exon = factor(p$Same_Comb_type_exon, 
                               levels = c("ncRNA","rRNA","yRNA", 
                                          "protein_coding: exon", "Repeat Element",
                                          "pseudogene","Antisense Feature",
                                          "protein_coding: Intron","lncRNA",
                                          "no Feature"))
p=subset(p, Same_Comb_type_exon == 'ncRNA')
if (nrow(p)>0) {
  
  u = unique(p$Same_Comb_type_ncRNA)
  
  #create new df
  pcount = data.frame(u,1:length(u))
  colnames(pcount)=c('Same_RNA_Subtype','Counts_All')
  
  #same note as above
  pcount$Counts_Unique=NA
  pcount$Counts_MM=NA
  pcount$Peak_count=NA

  for (x in 1:length(u)) {
    pam=p[p$Same_Comb_type_ncRNA%in%u[x],]
    pcount[x,1]=u[x]
    pcount[x,'Counts_Unique']=colSums(pam[,'Counts_Unique',drop=F],na.rm = T)
    pcount[x,'Counts_fracMM']=colSums(pam[,'Counts_fracMM',drop=F],na.rm = T)
    pcount[x,'Peak_count']=nrow(pam)
  }
  pcount$RNA=''
  
  gg1 = ggplot(pcount,
               aes(fill=Same_RNA_Subtype,x=RNA,y=Counts_Unique) ) +
    geom_bar(stat='identity',width=.5) +
    theme_classic()+ggtitle("ncRNA only: # of reads (unique) by catagory") + 
    labs(color='RNA Type') +
    scale_color_brewer(palette = "Paired") +
    scale_fill_brewer(palette = "Paired") +
    blank_theme + 
    coord_polar("y",start=0)
  
  gg2 = ggplot(pcount,
               aes(fill=Same_RNA_Subtype,x=RNA,y=Counts_fracMM) ) +
    geom_bar(stat='identity',width=.5) +
    theme_classic() +
    ggtitle("ncRNA only: # of reads (unique + Frac. MM) by catagory") +
    labs(color='RNA Type') +
    scale_color_brewer(palette = "Paired") +
    scale_fill_brewer(palette = "Paired") +  
    blank_theme+ 
    coord_polar("y",start=0)
  plot(gg1)
  plot(gg2)
}
```      
<!-- <font size="1">Columns: RNA_type_Classification + Counts_Unique </font>      -->
  
  <!-- <br>    -->
  
  <!-- ### Number of reads for each catagory   -->
  
  <br>   
  
```{r fig.asp=.5, fig.align='center',fig.height=4, fig.width=8,echo=F,warning=F,eval=T,include=F}

#version 7
p=Peaksdata2_anno
if (incd_rRNA==F) {
  p=susbet(p,!(Oppo_Comb_type_ncRNA == 'rRNA'))
}

###phil repeating similar code as above - can prob functionize this
#added if statement here
if(nrow(p)>0){
  u=unique(p$Oppo_Comb_type_exon)
  pcount=data.frame(u,1:length(u))
  colnames(pcount)=c('RNA_Type','Counts_All')
  
  #same note as above
  #pcount$Counts_Unique=NA
  #pcount$Counts_MM=NA
  #pcount$Peak_count=NA
  
  for (x in 1:length(u)) {
    pam=p[p$Oppo_Comb_type_exon%in%u[x],]
    pcount[x,1]=u[x]
    pcount[x,'Counts_Unique']=colSums(pam[,'Counts_Unique',drop=F],na.rm = T)
    pcount[x,'Counts_fracMM']=colSums(pam[,'Counts_fracMM',drop=F],na.rm = T)
    pcount[x,'Peak_count']=nrow(pam)
    
  }
  pcount$RNA=""
  
  gg = ggplot(pcount,aes(fill=RNA_Type,x=RNA,y=Counts_Unique) ) +
    geom_bar(stat='identity',position="stack",width=.5) +
    theme_classic() +
    ggtitle("BioType - # of reads (unique) by catagory)") +
    scale_fill_brewer(palette = "Dark2") 
  ggplotly(gg)
  
  gg = ggplot(pcount,aes(fill=RNA_Type,x=RNA,y=Counts_fracMM) ) +
    geom_bar(stat='identity',position="stack",width=.5) +
    theme_classic() +
    ggtitle("BioType - # of reads (Unique + Scaled Multimap) by catagory)") +
    scale_fill_brewer(palette = "Dark2")
  ggplotly(gg)
}
###phil need else statement - prob should just print something?
```


```{r fig.asp=.5, fig.align='center',fig.height=4, fig.width=8,echo=F,warning=F,eval=T,include=F}
#version 8
p=Peaksdata2_anno
if (incd_rRNA==F) {
  p=subset(p,!(Oppo_Comb_type_ncRNA == 'rRNA'))
}
p = subset(p,Oppo_Comb_type_exon == 'ncRNA')

if (nrow(p)>0) {
  u=unique(p$Oppo_Comb_type_ncRNA)
  
  pcount=data.frame(u,1:length(u))
  colnames(pcount)=c('RNA_Subtype','Counts_All')
  
  #same note
  pcount$Counts_Unique=NA
  pcount$Counts_MM=NA
  pcount$Peak_count=NA
  
  for (x in 1:length(u)) {
    pam=p[p$Oppo_Comb_type_ncRNA%in%u[x],]
    pcount[x,1]=u[x]
    pcount[x,'Counts_Unique']=colSums(pam[,'Counts_Unique',drop=F],na.rm = T)
    pcount[x,'Counts_fracMM']=colSums(pam[,'Counts_fracMM',drop=F],na.rm = T)
    pcount[x,'Peak_count']=nrow(pam)
  }
  
  pcount$RNA=''

  gg = ggplot(pcount,aes(fill=RNA_Subtype,x=RNA,y=Counts_Unique) ) +
    geom_bar(stat='identity',width=.5) +
    theme_classic() +
    ggtitle("ncRNA only: # of reads (unique) by catagory") +
    scale_color_brewer(palette = "Paired")+scale_fill_brewer(palette = "Paired") +  
    blank_theme + 
    coord_polar("y",start=0)
  gg
  
  gg = ggplot(pcount,aes(fill=RNA_Subtype,x=RNA,y=Counts_fracMM) )+geom_bar(stat='identity',width=.5) + 
    theme_classic() +
    ggtitle("ncRNA only: # of reads (Scaled Multimap) by catagory") +
    scale_color_brewer(palette = "Paired") +
    scale_fill_brewer(palette = "Paired") +  
    blank_theme+ 
    coord_polar("y",start=0)
  gg
}
```      
<!-- <font size="1">Columns: Opposite Strand: RNA_type </font>      -->
  
  
  <!-- ## Identify Alternative Mapping locations for Multimapped reads -->
```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,include=F}
###phil we write out this table but don't use it?
#file=paste0(params$OutDIR,"/ALTmap/CLIP_",samplename,"_",params$PeakIdnt,"Peaks",ntmerge,'_peakDepth',
#params$readdepth,params$NameAdd,"_ALT_IN.txt"), 
write.table(Peaksdata2_anno[,c('chr','start','end','strand','ID',
                               'Same_gene_name_comb','Same_ensembl_gene_id',
                               'Counts_Unique','Counts_MM',
                               'Same_Comb_type_ncRNA','Same_Comb_type_exon')],
            file=paste0(out_diparams$OutDIR,"/ALTmap/CLIP_",samplename,"_",
                        params$PeakIdnt,"Peaks",ntmerge,'_peakDepth',
                        params$readdepth,params$NameAdd,"_ALT_IN.txt"), 
            sep = "\t", row.names = FALSE, 
            col.names = T, append = F, quote= FALSE,na = "")

###phil - do we need this code since it's set to False?
#SSC did not clean or review
calcALTLOC=F
if (calcALTLOC==T) {
  
  BamMM=readGAlignments(paste0(INbam,'multimap/',samplename,'_Clip_iCountcutadpt_all.unique.NH.mm.ddup.mm.bam'),use.names=T)
  
  mcols(BamMM)$qname=names(BamMM)
  
  Peaksdata2_anno.GR = GRanges(seqnames = as.character(Peaksdata2_anno$chr), ranges=IRanges(start = as.numeric(Peaksdata2_anno$start), end = as.numeric(Peaksdata2_anno$end)),strand = Peaksdata2_anno$strand,
                               ID=Peaksdata2_anno$ID,
                               Same_Host_gene_name=Peaksdata2_anno$Same_gene_name_comb,
                               Same_Host_gene_ensembl_id=Peaksdata2_anno$Same_ensembl_gene_id,
                               counts_Ro=Peaksdata2_anno$Counts_Unique,
                               Same_Comb_type_ncRNA=Peaksdata2_anno$Same_Comb_type_ncRNA,
                               Same_Comb_type_exon=Peaksdata2_anno$Same_Comb_type_exon)
  
  q = Peaksdata2_anno.GR
  s = BamMM
  xo=as.data.frame(GenomicRanges::findOverlaps(q,s,type = "any",ignore.strand=T),row.names = NULL)
  
  qh=as.data.frame(q[xo$queryHits],row.names = NULL)
  colnames(qh)=paste0(colnames(qh),"_peaks")
  sh=as.data.frame(s[xo$subjectHits],row.names = NULL)
  colnames(sh)=paste0(colnames(sh),"_bam")
  bamMM_anno=cbind(qh,sh)
  
  
  Peaksdata2_MM=Peaksdata2_anno[Peaksdata2_anno$Counts_MM>1,]
  Peaksdata2_MM=Peaksdata2_MM[Peaksdata2_MM$Same_Comb_type_exon%in%'ncRNA',]
  out=as.data.frame(matrix(nrow=nrow(Peaksdata2_MM),ncol=12));
  colnames(out)=c("ID","Peak_type","Number_ALLMM","MultiMappers_ncRNA_type",
                  'Number_MMinpeak','Number_MMoutpeak',"Number_AltMappings",
                  'Number_Altlocations',"Altlocations","Number_Altlocations_SamePeaktype",
                  "Number_Altlocations_DifferentPeaktype","Perc_DifferentPeaktype")
  
  for (x in 1:nrow(Peaksdata2_MM)) {
    
    PL=Peaksdata2_MM[x,]
    PL.GR = GRanges(seqnames = as.character(PL$chr), 
                    ranges=IRanges(start = as.numeric(PL$start), 
                                   end = as.numeric(PL$end)),
                    strand = PL$strand,
                    ID=PL$ID,
                    counts_Ro=PL$Counts_Unique,
                    Same_Host_gene_name=as.character(PL$Same_gene_name_comb),
                    Same_Host_gene_ensembl_id=as.character(PL$Same_ensembl_gene_id),
                    Same_Comb_type_ncRNA=as.character(PL$Same_Comb_type_ncRNA),
                    Same_Comb_type_exon=as.character(PL$Same_Comb_type_exon))
    q = PL.GR
    s = BamMM
    
    xo=as.data.frame(GenomicRanges::findOverlaps(q,s,type = "any",ignore.strand=T))
    qh=as.data.frame(q[xo$queryHits],row.names = NULL)
    colnames(qh)=paste0(colnames(qh),"_peaks")
    sh=as.data.frame(s[xo$subjectHits],row.names = NULL)
    colnames(sh)=paste0(colnames(sh),"_bam")
    bam_PL=cbind(qh,sh)
    
    Peak_MultiMappers=bamMM_anno[bamMM_anno$qname_bam%in%bam_PL$qname_bam,]
    Peak_MultiMappers[is.na(Peak_MultiMappers$Same_Comb_type_ncRNA_peaks),'Same_Comb_type_ncRNA_peaks'] =
      as.character(Peak_MultiMappers[is.na(Peak_MultiMappers$Same_Comb_type_ncRNA_peaks),'Same_Comb_type_exon_peaks'])
    
    out[x,'ID']=PL$ID
    out[x,'Peak_type']=PL$Same_Comb_type_ncRNA
    m_NC_BT=unique(Peak_MultiMappers$Same_Comb_type_ncRNA_peaks)
    m_NC_BT=m_NC_BT[is.na(m_NC_BT)==F]
    out[x,'MultiMappers_ncRNA_type']=paste0(m_NC_BT,collapse = ', ')
    out[x,'Number_ALLMM']=nrow(Peak_MultiMappers)
    out[x,'Number_MMinpeak']=length(bam_PL$qname_bam)
    out[x,'Number_MMoutpeak']=nrow(Peak_MultiMappers[!Peak_MultiMappers$ID%in%PL$ID,])
    out[x,'Number_AltMappings']=nrow(Peak_MultiMappers)-PL$Counts_MM
    out[x,'Number_Altlocations']=length(unique(Peak_MultiMappers[!Peak_MultiMappers$ID%in%PL$ID,"ID_peaks"]))
    
    out[x,
        c('Altlocations','Number_Altlocations_SamePeaktype',
          'Number_Altlocations_DifferentPeaktype','Perc_DifferentPeaktype')]=NA    
    
    ALTLOC=((Peak_MultiMappers[!Peak_MultiMappers$ID_peaks%in%PL$ID,]))
    if (nrow(ALTLOC)>0) {
      ALTLOC$ALTLOCname=paste0(ALTLOC$ID_peaks,'_',ALTLOC$Same_Comb_type_ncRNA_peaks)
      ALTLOCname=unique(ALTLOC$ALTLOCname)
      ALTLOCname=ALTLOCname[is.na(ALTLOCname)==F]
      out[x,'Altlocations']=paste0(ALTLOCname,collapse = ", ")
      Peak_MultiMappers_AltLoc=Peak_MultiMappers[Peak_MultiMappers$ID_peaks%in%unique(ALTLOC$ID_peaks),]
      
      out[x,'Number_Altlocations_SamePeaktype']=nrow(Peak_MultiMappers_AltLoc[Peak_MultiMappers_AltLoc$Same_Comb_type_ncRNA_peaks%in%(PL$Same_Comb_type_ncRNA),])
      out[x,'Number_Altlocations_DifferentPeaktype']=nrow(Peak_MultiMappers_AltLoc[!Peak_MultiMappers_AltLoc$Same_Comb_type_ncRNA_peaks%in%(PL$Same_Comb_type_ncRNA),])
      out[x,'Perc_DifferentPeaktype']=(out[x,'Number_Altlocations_DifferentPeaktype']/out[x,'Number_MMoutpeak'])*100
    }
    if (x%in%seq(from = 0, to = 10000, by = 50)) {
      print(x/nrow(Peaksdata2_MM))       
    }
  }
  
  out=out[!is.na(out$Altlocations),]
  Peaksdata2_alt=out[,c("ID","Number_MMoutpeak",'Number_Altlocations_DifferentPeaktype','Number_Altlocations_SamePeaktype','MultiMappers_ncRNA_type','Perc_DifferentPeaktype','Altlocations')]
  colnames(Peaksdata2_alt)=
    c("ID","MM_number",'MM_Alt_Peaktype','MM_Same_Peaktype','MM_type','MM_Prec_Alt_Peaktype','MM_Alt_Alignments')
  Peaksdata2_alt=merge(Peaksdata2_anno,Peaksdata2_alt,by='ID',all.x=T)
}

###phil - i assumed that we were using this one instead, but we have not generated this file...
###need to figure out where this code comes from, generate this output and continue
calcALTLOC=F
if (calcALTLOC==F) {
  
  Peaksdata2_alt = fread(paste0('./ALTmap/CLIP_',samplename,'Peaks_',
                                samplename,'ALTloc_OUT.txt'), header=T, sep="\t",
                         stringsAsFactors = F,data.table=F)
  Peaksdata2_alt=merge(Peaksdata2_anno,Peaksdata2_alt,by='ID',all.x=T)
}

###fix variable swap
Peaksdata2_anno=Peaksdata2_alt

```

<!-- # Pvalue of peak detection   -->
```{r ,fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,include=F}
if (RunMAnorm==TRUE) {
  
  ###input bed file
  #paste0('./peaks_ctk/',
   #                      samplename,'/',
  #                       samplename,'_Clip_iCountcutadpt_all.unique.NH.mm.ddup.unique.sig.boundary.bed')
  ###phil i don't know where this bed file is coming from?
  PeaksPVal=fread(manorm_bed_path,
                  header=T, sep="\t",stringsAsFactors = F,data.table=F)
  
  colnames(PeaksPVal)=c('chr','start','end','anno','count','strand')
  PeaksPVal=separate(PeaksPVal,anno,sep='\\]\\[',into=c('CDKpeak','PH','PH0','Pval'))
  PeaksPVal$PH=gsub("PH=","",PeaksPVal$PH);PeaksPVal$PH=as.numeric(PeaksPVal$PH)
  PeaksPVal$PH0=gsub("PH0=","",PeaksPVal$PH0);PeaksPVal$PH0=as.numeric(PeaksPVal$PH0)
  PeaksPVal$Pval=gsub("P=", "",
                      PeaksPVal$Pval);PeaksPVal$Pval=gsub("\\]","",PeaksPVal$Pval);PeaksPVal$Pval=as.numeric(PeaksPVal$Pval)
  PeaksPVal=PeaksPVal[PeaksPVal$count>=5,]
  
  PeaksPVal$ID_ctk=paste0(PeaksPVal$chr,':',PeaksPVal$start,'-',PeaksPVal$end)
  dup=PeaksPVal[duplicated(PeaksPVal$ID_ctk),'ID_ctk']
  dup=unique(dup)
  
  dupOUT=as.data.frame(matrix(nrow=length(unique(dup)),
                              ncol=ncol(PeaksPVal)));colnames(dupOUT)=colnames(PeaksPVal)
  dupOUT$numPval=NA
  dupOUT$numPvalequal=NA
  
  for (l in 1:length(dup)) {
    l1=PeaksPVal[PeaksPVal$ID_ctk%in%dup[l],]
    dupOUT[l,'numPval']=nrow(l1)
    
    l2=l1[l1$Pval%in%(min(l1$Pval)),]
    dupOUT[l,'numPvalequal']=nrow(l2)-1
    
    l2=l2[order(l2$Pval,decreasing = F),]
    dupOUT[l,1:ncol(l2)]=l2[1,1:ncol(l2)]
  }
  
  PeaksPVal=rbind(PeaksPVal[PeaksPVal$ID_ctk%in%unique(dup)==F,],dupOUT[,colnames(PeaksPVal)])
  Peaks.GR <- GRanges(seqnames = as.character(Peaksdata2_anno$chr), ranges=IRanges(start = as.numeric(Peaksdata2_anno$start), end = as.numeric(Peaksdata2_anno$end)),strand = Peaksdata2_anno$strand,ID=Peaksdata2_anno$ID )
  
  Annotable=PeaksPVal    
  anno.GR <- GRanges(seqnames = as.character(Annotable$chr), ranges=IRanges(start = as.numeric(Annotable$start), end = as.numeric(Annotable$end)),strand = as.character(Annotable$strand),
                     Pval=Annotable$Pval,
                     ID_ctk=Annotable$ID_ctk
  )
  
  q =Peaks.GR
  s=anno.GR
  xo=as.data.frame(GenomicRanges::findOverlaps(q,s,type = "any",minoverlap=.9,ignore.strand=F))
  sh=as.data.frame(s[xo$subjectHits]);colnames(sh)=paste0(colnames(sh),'_ctk')
  qh=as.data.frame(q[xo$queryHits])
  PeaksPVal_Out=cbind(sh,qh)
  
  dupxo=unique(PeaksPVal_Out[duplicated(PeaksPVal_Out$ID),'ID'])
  
  dupOUT2=as.data.frame(matrix(nrow=length(unique(dupxo)),
                               ncol=ncol(PeaksPVal_Out)));colnames(dupOUT2)=colnames(PeaksPVal_Out)
  dupOUT2$numPval=NA
  dupOUT2$numPvalequal=NA
  
  for (l in 1:length(dupxo)) {
    l1=PeaksPVal_Out[PeaksPVal_Out$ID%in%dupxo[l],]
    dupOUT2[l,'numPval']=nrow(l1)
    
    l2=l1[l1$Pval%in%(min(l1$Pval)),]
    dupOUT2[l,'numPvalequal']=nrow(l2)-1
    
    l2=l2[order(l2$Pval,decreasing = F),]
    dupOUT2[l,1:ncol(l2)]=l2[1,1:ncol(l2)]
  }
  
  PeaksPVal_Out=rbind(PeaksPVal_Out[PeaksPVal_Out$ID%in%unique(dupOUT2$ID)==F,],
                      dupOUT2[,colnames(PeaksPVal_Out)])
  length(unique(PeaksPVal_Out$ID))
}

```

<!-- <br> -->
  
  
  <!-- **3. Calculate relative location of CLIP peak in Intron or Exon** -->
  
  <!--   Use 5'most nt in CLIP peak -->

<!--   Calculate position of CLIP peak in exon/intron feature.   -->

<!-- <br>   -->

```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,include=T}
pp = Peaksdata2_anno[ ,
                      c("ID","Geneid","strand","Counts_Unique",'Same_Intron_start_dist',
                        'Same_Exn_start_dist','Comb_type_exon_Oppo','Same_type_comb',
                        'Same_Repeat_comb','Same_Comb_type_exon','Same_Comb_type_ncRNA',
                        'Oppo_type_comb','Oppo_Repeat_comb','Oppo_Comb_type_exon',
                        'Oppo_Comb_type_ncRNA') ]
pp=pp[is.na(pp$Same_Repeat_comb),]

ggplot(pp,
       aes(x=Same_Intron_start_dist) ) + 
  geom_density(size=2)+theme_classic() +
  ggtitle("Location of CLIP Peak in Intron") +
  xlab("Relative Intron Location of CLIP Peak - 5' to 3' (%)") +
  xlim(-10,110) +
  theme(plot.title = element_text(hjust = 0.5,
                                  size = 25),
        axis.title=element_text(size=20), axis.text=element_text(size=15),
        legend.text = element_text( size=30))

ggplot(pp,
       aes(x=Same_Exn_start_dist) ) + 
  geom_density(size=2)+theme_classic() +
  ggtitle("Location of CLIP Peak in Exon") +
  xlab("Relative Exon Location of CLIP Peak - 5' to 3' (%)") +
  xlim(-10,110) +
  theme(plot.title = element_text(hjust = 0.5,
                                  size = 25),
        axis.title=element_text(size=20),
        axis.text=element_text(size=15),legend.text = element_text( size=30))
```

```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F, warning=F, eval=F}
p=Peaksdata2

ppx=p[p$overlap_class=='exon',];ppx=ppx[is.na(ppx[,1])==F,]
ppx=unlist(stri_split_fixed(ppx$Exn_jx_updist,","))
ppx=gsub(" ","",ppx);ppx=ppx=gsub("_NA","",ppx);ppx=ppx=gsub("NA","",ppx)
ppx=as.data.frame(ppx[ppx!=""])
colnames(ppx)[1]="pp"
ppx=ppx[is.na(ppx$pp)==F,,drop=F]
ppx$pp=as.numeric(as.character(ppx$pp))
ppx=cbind(matrix(nrow = nrow(ppx),'exon'),ppx);colnames(ppx)=c("Overlap_Type",'pp')
pp=ppx
```

<!-- # Compare to previous Peak detection    -->
<!-- <br>   -->
<!-- <br>   -->

```{r ,fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,include=F}
Peaksdata_original=fread('CLIP_Peaks_MD4.txt', header=T, sep="\t",stringsAsFactors = F,data.table=F)
Peaksdata_original=separate(Peaksdata_original,ID,into = c('chr','start'),sep=':',remove = F)
Peaksdata_original=separate(Peaksdata_original,start,into = c('start','end'),sep='-',remove = F)
Peaksdata_original$start=as.numeric(Peaksdata_original$start)
Peaksdata_original$end=as.numeric(Peaksdata_original$end)

#################################################
iCount=fread('CLIP_Peaks_MD4_iCounts.txt', header=T, sep="\t",stringsAsFactors = F,data.table=F)
iCount=separate(iCount,ID,into = c('chr','start'),sep=':',remove = F)
iCount=separate(iCount,start,into = c('start','end'),sep='-',remove = F)
iCount$start=as.numeric(iCount$start)
iCount$end=as.numeric(iCount$end)

#######
iClip_range=fread('CLIP_Peaks_MD4_iCounts_locations_range.txt', header=T, sep="\t",stringsAsFactors = F,data.table=F)
iClip_range$V1=paste0('chr',iClip_range$V1)

colnames(iClip_range)[colnames(iClip_range)%in%'V2']='start_range'
colnames(iClip_range)[colnames(iClip_range)%in%'V3']='end_range'
iCount=merge(iCount,iClip_range,by.x='ID',by.y='V1')
```

```{r ,echo=F,warning=F,warning=T,eval=F,include=F}
Peaksdata4$start=as.numeric(Peaksdata4$start)
Peaksdata4$end=as.numeric(Peaksdata4$end)

Peaksdata4.GR = GRanges(seqnames = as.character(Peaksdata4$chr), ranges=IRanges(start = as.numeric(Peaksdata4$start), end = as.numeric(Peaksdata4$end)),strand = Peaksdata4$strand,
                   ID=Peaksdata4$ID,
                   Same_Host_gene_name=Peaksdata4$`Same Strand: Host_gene_name`,
                   Same_Host_gene_ensembl_id=Peaksdata4$`Same Strand: Host_gene_ensembl_id`,
                    counts_Ro=Peaksdata4$Counts_Unique)

```

```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,include=F}

iCount_clust2_range=fread('CLIP_Peaks_MD4_iCounts_locations_range.txt', header=T, sep="\t",stringsAsFactors = F,data.table=F)
colnames(iCount_clust2_range)=c('ID','Start_range','End_range','chr','ID_range')
iCount_clust2_range$ID=paste0('chr',iCount_clust2_range$ID)
iCount_clust2_range=separate(iCount_clust2_range,col = ID,into =c( 'chr'),sep = ':',remove = F)
iCount_clust2_range$Start_range=iCount_clust2_range$Start_range-0
iCount_clust2_range$End_rangeiCount_clust2_range$End_range+0
iCount_clust2_range$ID_range =paste0(iCount_clust2_range$chr,':',iCount_clust2_range$Start_range,'-',iCount_clust2_range$End_range)

iCount_clust2_adj=merge(iCount,iCount_clust2_range[c('ID','Start_range','End_range','ID_range')],by='ID')
iCount_clust2_adj=iCount_clust2_adj[duplicated(iCount_clust2_adj$ID)==F,]

```

```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,include=F}
iCount_clust=iCount_clust2_adj
iCount_clust.GR = GRanges(seqnames = as.character(iCount_clust$chr), ranges=IRanges(start = as.numeric(iCount_clust$start)-0, end = as.numeric(iCount_clust$end)+0),strand = iCount_clust$strand,
                   ID=iCount_clust$ID,
                   count=iCount_clust$counts_Ro)

q = Peaksdata4.GR
s = iCount_clust.GR
xo=as.data.frame(GenomicRanges::findOverlaps(q,s,type = "any",ignore.strand=T))
          
qh=as.data.frame(q[xo$queryHits],row.names = NULL)
colnames(qh)=paste0(colnames(qh),"_peaks")
sh=as.data.frame(s[xo$subjectHits],row.names = NULL)
colnames(sh)=paste0(colnames(sh),"_iCount")
peaks_iCount=cbind(qh,sh)
        
Peaksdata4$iCount_peak=0
Peaksdata4[Peaksdata4$ID%in%unique(peaks_iCount$ID_peaks),'iCount_peak']=1
iCount_clust$NovoCount=0
iCount_clust[iCount_clust$ID%in%qh$ID_iCounr==T,"NovoCount"]=1
iCount_clust3=merge(iCount_clust,peaks_iCount[,c('ID_peaks','ID_iCount')],all.x=T,by.x='ID',by.y='ID_iCount')
  
Clip_Comb=merge(Peaksdata4,iCount_clust3,by.x='ID',by.y='ID_peaks',all=T,suffix=c('_Custom','_iCount'))
Clip_Comb=Clip_Comb[!duplicated(Clip_Comb),]

iCount_only=iCount_clust[!iCount_clust.GR$ID%in%peaks_iCount$ID_iCount,]
Peaks_only=Peaksdata4[!Peaksdata4$ID%in%peaks_iCount$ID_peaks,]
intersect=peaks_iCount
```

```{r  fig.align='center' ,echo=F,warning=F,eval=F,include=F}
Clip_Comb_venn=Clip_Comb
Clip_Comb_venn$ID_ALL=paste0(Clip_Comb_venn$ID,'_',Clip_Comb_venn$ID_iCount)

a=Clip_Comb_venn[is.na(Clip_Comb_venn$ID)==F,'ID_ALL']
  a=a[is.na(a)==F]
  a=unique(a)
b=Clip_Comb_venn[is.na(Clip_Comb_venn$ID_iCount)==F,'ID_ALL']
  b=b[is.na(b)==F]
    b=unique(b)

OVLG_all=unique(c(a,b))
OVLG_all=OVLG_all[is.na(OVLG_all)==F]

a=OVLG_all%in%a
b=OVLG_all%in%b

C3=cbind(a,b)

rownames(C3)=OVLG_all;colnames(C3)=c('Custom Peak Calling(Novoalign)','ICount peaks')
{vennDiagram(vennCounts(C3),
            circle.col = c("red", "blue", "green3",'orange'),
            cex = 1)
remove(a,b,c,OVLG_all,C3)
  title('Compare Peak calling methods')}

iCount_only=iCount_clust2_adj[!iCount_clust2_adj$ID%in%peaks_iCount$ID_iCount,]
Peaks_only=Peaksdata4[!Peaksdata4$ID%in%unique(peaks_iCount$ID_peaks),]
intersect=iCount_clust2_adj[iCount_clust2_adj$ID%in%peaks_iCount$ID_iCount,]
```

```{r fig.asp=.5, fig.align='center',fig.height=3, fig.width=6,echo=F,warning=F,eval=F,include=F}

iCount$Peak_width=abs(iCount$end_range-iCount$start_range)
Peaksdata2$Peak_width=abs(as.numeric(Peaksdata2$end)-as.numeric(Peaksdata2$start))
Peaksdata2$method='NovoAlign_UMItools'
iCount$method='iCount'


CombMethod=rbind(Peaksdata2[,c('method','Peak_width')],iCount[,c('method','Peak_width')])
ggplot(CombMethod,
       aes(x=Peak_width,line=method,color=method) ) +
  geom_density(size=2)+theme_classic() +
  ggtitle("Peak Width")+xlab("Width (nt)") + 
  xlim(-10,110) +
  theme(plot.title = element_text(hjust = 0.5,
                                  size = 25),
        axis.title=element_text(size=20), axis.text=element_text(size=15),
        legend.text = element_text( size=30))
```

<br>   

<br>   

### Read Counts by peak for each catagory    
  
#### Unique Read counts (Count Unique reads only)   

<br>   

```{r fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=T, include=T}
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
if (incd_rRNA==F) {
  p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
}

colnames(p)[colnames(p)%in%'Same_Comb_type_exon']='RNA_Type'
p$RNA=''
 gg=ggplot(p,aes(x=RNA_Type,y=Counts_Unique,fill=RNA_Type) )+geom_violin()+theme_classic()+geom_jitter(height = 0, width = 0.1,size=1)+
  scale_y_continuous(trans = "log2")+
  ggtitle('Peak Counts (Unique) for Ro-Clip\nby Feature')+ylab("Counts - Ro-Clip")+xlab("")+
theme(plot.title = element_text(hjust = 0.5,size = 25),axis.title=element_text(size=20),axis.text=element_text(size=15))+theme(legend.position = "none") +
    theme(axis.text.x = element_text(angle = -45))
# 
gg
```  
<!-- <font size="1">Columns: RNA_type_Classification </font>      -->
<br/>    

<!-- no Feature peaks with counts > 20 = `r nrow(Peaksdata2_anno[Peaksdata2_anno$Counts_Unique>20&(Peaksdata2_anno$Comb_type_exon_Oppo%in%'no Feature'),])`   -->

<br/>    

```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=8,echo=F,warning=F,eval=T, include=T}
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
# if (incd_rRNA==F) {
#   p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
# }

p=p[p$Same_Comb_type_exon%in%'ncRNA',]

if (nrow(p)>0) {

p$ID_name=paste0(p$ID,"\n",p$Same_gene_name_comb)


colnames(p)[colnames(p)%in%'Same_Comb_type_ncRNA']='RNA_Type'


 gg=ggplot(p,aes(x=RNA_Type,y=Counts_Unique,fill=RNA_Type) )+geom_violin()+theme_classic()+geom_jitter(height = 0, width = 0.1,size=0.5,aes(text=ID_name))+
  scale_y_continuous(trans = "log2")+
  ggtitle('Peak Counts (Unique) for Ro-Clip\nby Feature')+ylab("Counts - Ro-Clip")+xlab("")+
theme(plot.title = element_text(hjust = 0.5,size = 15),axis.title=element_text(size=15),axis.text=element_text(size=12))+theme(legend.position = "none") +
    theme(axis.text.x = element_text(angle = -45))+scale_fill_brewer(palette = "Paired")
 ggplotly(gg,tooltip = c("text", "y"))
}
```  
<br>   
<br>   

#### Fractional Multimap Read counts (Count Unique reads + (MultiMapped read / # of different mappings) )     

Does include rRNA
<br>   

```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=T}
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
# if (incd_rRNA==F) {
#   p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
# }

colnames(p)[colnames(p)%in%'Same_Comb_type_exon']='RNA_Type'
p$RNA=''
 gg=ggplot(p,aes(x=RNA_Type,y=Counts_fracMM,fill=RNA_Type) )+geom_violin()+theme_classic()+geom_jitter(height = 0, width = 0.1,size=1)+
  scale_y_continuous(trans = "log2")+
  ggtitle('Peak Counts (Unique + Frac. MM) for Ro-Clip\nby Feature')+ylab("Counts - Ro-Clip")+xlab("")+
theme(plot.title = element_text(hjust = 0.5,size = 25),axis.title=element_text(size=20),axis.text=element_text(size=15))+theme(legend.position = "none") +
    theme(axis.text.x = element_text(angle = -45))
# 
gg
```  
<!-- <font size="1">Columns: RNA_type_Classification </font>      -->
<br/>    

<!-- no Feature peaks with counts > 20 = `r nrow(Peaksdata2_anno[Peaksdata2_anno$Counts_fracMM>20&(Peaksdata2_anno$Comb_type_exon_Oppo%in%'no Feature'),])`   -->

<br/>    

```{r fig.asp=.5,fig.align='center',fig.height=6, fig.width=8,echo=F,warning=F,eval=T}
p=Peaksdata2_anno
p$Same_Comb_type_exon=p$Comb_type_exon_Oppo
# if (incd_rRNA==F) {
#   p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
# }

p=p[p$Same_Comb_type_exon%in%'ncRNA',]
if (nrow(p)>0) {

colnames(p)[colnames(p)%in%'Same_Comb_type_ncRNA']='RNA_Type'
p$ID_name=paste0(p$ID,"\n",p$Same_gene_name_comb)

 gg=ggplot(p,aes(x=RNA_Type,y=Counts_fracMM,fill=RNA_Type) )+geom_violin()+theme_classic()+geom_jitter(height = 0, width = 0.05,size=.5,aes(text=ID_name))+
  scale_y_continuous(trans = "log2")+
  ggtitle('Peak Counts (Unique + Frac. MM) for Ro-Clip\nby ncRNA Type')+ylab("Counts - Ro-Clip")+xlab("")+
theme(plot.title = element_text(hjust = 0.5,size = 15),axis.title=element_text(size=15),axis.text=element_text(size=12))+theme(legend.position = "none") +
    theme(axis.text.x = element_text(angle = -45))+scale_fill_brewer(palette = "Paired")

 ggplotly(gg,tooltip = c("text", "y"))
 
}
```  
<br>   
<br>   

<!-- #### Best Mapped Read counts (Unique reads + Best mapping location for MM reads ) -->

<!-- Multimapped reads are only assigned to best mapping location and get a count of 1. -->

<!-- <br> -->

<!-- ```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=T } -->
<!-- p=Peaksdata2_anno -->
<!-- p$Same_Comb_type_exon=p$Comb_type_exon_Oppo -->
<!-- # if (incd_rRNA==F) { -->
<!-- #   p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA')) -->
<!-- # } -->

<!-- colnames(p)[colnames(p)%in%'Same_Comb_type_exon']='RNA_Type' -->
<!-- p$RNA='' -->
<!--  gg=ggplot(p,aes(x=RNA_Type,y=Counts_primary,fill=RNA_Type) )+geom_violin()+theme_classic()+geom_jitter(height = 0, width = 0.1,size=1)+ -->
<!--   scale_y_continuous(trans = "log2")+ -->
<!--   ggtitle('Peak Counts (Unique + Best Mapped MM) for Ro-Clip\nby Feature')+ylab("Counts - Ro-Clip")+xlab("")+ -->
<!-- theme(plot.title = element_text(hjust = 0.5,size = 25),axis.title=element_text(size=20),axis.text=element_text(size=15))+theme(legend.position = "none") + -->
<!--     theme(axis.text.x = element_text(angle = -45)) -->
<!-- # -->
<!-- gg -->
<!-- ``` -->
<!-- <br/> -->


<!-- <br/> -->

<!-- ```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=8,echo=F,warning=F,eval=T} -->
<!-- p=Peaksdata2_anno -->
<!-- p$Same_Comb_type_exon=p$Comb_type_exon_Oppo -->
<!-- # if (incd_rRNA==F) { -->
<!-- #   p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA')) -->
<!-- # } -->

<!-- p=p[p$Same_Comb_type_exon%in%'ncRNA',] -->
<!-- colnames(p)[colnames(p)%in%'Same_Comb_type_ncRNA']='RNA_Type' -->
<!-- p$ID_name=paste0(p$ID,"\n",p$Same_gene_name_comb) -->

<!--  gg=ggplot(p,aes(x=RNA_Type,y=Counts_primary,fill=RNA_Type) )+geom_violin()+theme_classic()+geom_jitter(height = 0, width = 0.05,size=.5,aes(text=ID_name))+ -->
<!--   scale_y_continuous(trans = "log2")+ -->
<!--   ggtitle('Peak Counts (Unique + Best Mapped MM) for Ro-Clip\nby ncRNA Type')+ylab("Counts - Ro-Clip")+xlab("")+ -->
<!-- theme(plot.title = element_text(hjust = 0.5,size = 15),axis.title=element_text(size=15),axis.text=element_text(size=12))+theme(legend.position = "none") + -->
<!--     theme(axis.text.x = element_text(angle = -45))+scale_fill_brewer(palette = "Paired") -->

<!--  ggplotly(gg,tooltip = c("text", "y")) -->
<!-- ``` -->
<!-- <br> -->
<!-- <br> -->

<!-- #### % Multimapped reads for each peak -->

<!-- <br> -->
<!-- ```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,incude=F} -->
<!-- p=Peaksdata2_anno -->
<!-- p$Same_Comb_type_exon=p$Comb_type_exon_Oppo -->
<!-- if (incd_rRNA==F) { -->
<!--   p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA')) -->
<!-- } -->

<!-- colnames(p)[colnames(p)%in%'Same_Comb_type_exon']='RNA_Type' -->
<!-- p$RNA='' -->
<!--  gg=ggplot(p,aes(x=RNA_Type,y=perc_mm,fill=RNA_Type) )+geom_violin()+theme_classic()+geom_jitter( width = 0.1,size=1)+ -->
<!--   ggtitle('Peak % Multimapped reads for Ro-Clip\nby Feature')+ylab("% multimapped reads - Ro-Clip")+xlab("")+ -->
<!-- theme(plot.title = element_text(hjust = 0.5,size = 25),axis.title=element_text(size=20),axis.text=element_text(size=15))+theme(legend.position = "none") + -->
<!--     theme(axis.text.x = element_text(angle = -45)) -->
<!-- gg -->

<!-- ``` -->

<!-- ```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,incude=F} -->
<!-- p=Peaksdata2_anno -->
<!-- p$Same_Comb_type_exon=p$Comb_type_exon_Oppo -->
<!-- if (incd_rRNA==F) { -->
<!--   p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA')) -->
<!-- } -->

<!-- p=p[p$Same_Comb_type_exon%in%'ncRNA',] -->
<!-- colnames(p)[colnames(p)%in%'Same_Comb_type_ncRNA']='RNA_Type' -->


<!--  gg=ggplot(p,aes(x=RNA_Type,y=perc_mm,fill=RNA_Type) )+geom_violin()+theme_classic()+geom_jitter( width = 0.1,size=1)+ -->
<!--   ggtitle('Peak % Multimapped reads for Ro-Clip\nby ncRNA Type')+ylab("% multimapped reads - Ro-Clip")+xlab("")+ -->
<!-- theme(plot.title = element_text(hjust = 0.5,size = 15),axis.title=element_text(size=15),axis.text=element_text(size=12))+theme(legend.position = "none") + -->
<!--     theme(axis.text.x = element_text(angle = -45))+scale_fill_brewer(palette = "Paired") -->

<!-- gg -->
<!-- ``` -->


<br>  


## Opposite strand CLIP peak attributes   
```{r , fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F}

p=Peaksdata2_anno
p=p[p$Comb_type_exon_Oppo%in%'Antisense Feature',]
if (incd_rRNA==F) {
  p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
}

colnames(p)[colnames(p)%in%'Oppo_Comb_type_exon']='RNA_Type'
p$RNA=''

ggplot(p,
       aes(fill=RNA_Type,x=RNA_Type) ) + 
  geom_bar(stat="count")+theme_classic() +
  ggtitle("Opposite Strand Feature - Number of peaks by catagory\n(Determined by unique reads only)") +
  xlab("") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title=element_text(size=15),axis.text=element_text(size=10),
        legend.position = "none",axis.text.x = element_text(angle = -45,vjust = .5)) +
  scale_fill_brewer(palette = "Dark2") 
```

```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=T,incude=T}

p=Peaksdata2_anno
if (incd_rRNA==F) {
  p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA'))
}
p$transition=paste0(p$Same_Comb_type_exon,'->\n',p$Oppo_Comb_type_exon)
p=p[p$Comb_type_exon_Oppo%in%'Antisense Feature',]
colnames(p)[colnames(p)%in%'transition']='RNA_Type'
p$Difference=''

ggplot(p,
       aes(fill=Same_Comb_type_exon,x=factor(Oppo_Comb_type_exon)) ) +
  geom_bar(stat="count") +
  theme_classic() +
  ggtitle("Opposite Strand Feature Features: \n Compare Antisense and Snese stand Annotation") + 
  xlab("Antisense strand Annotation") +
  ylab("Peak Count") +
  labs(fill = "Sense Stand Annotation") +
  theme(plot.title = element_text(hjust = 0.5,size=20),
      axis.title=element_text(size=15),
      axis.text=element_text(size=10),
      legend.position = "right",
      axis.text.x = element_text(angle = -45,vjust = .5))
```

<br>  

```{r echo=F,warning=F, include=T,eval=T}
p=as.data.frame(((colSums(is.na(Peaksdata2_anno[,grep('Oppo_Repeat_',colnames(Peaksdata2_anno))])==F))))
p$Repeat_Type=rownames(p);colnames(p)=c('Frequency','Repeat_Type')
p=p[rownames(p)%in%'Oppo_Repeat_comb'==F,]
p$Repeat_Type=gsub("Oppo_Repeat_","",p$Repeat_Type)

ggplot(p )+geom_bar(aes(x=Repeat_Type,y=Frequency),stat="identity") +
  theme_classic() +
  xlab("") +
  ylab("number of peaks in \nrepeat regions") +
  ggtitle("Opposite Strand") +
  theme(plot.title = element_text(hjust = 0.5,size = 15),
      axis.title=element_text(size=15),
      axis.text=element_text(size=10),
      legend.text = element_text( size=10)) +
  theme(axis.text.x = element_text(angle = -45))

```

```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=T,include=F}
#RUN2

if (params$Condense==FALSE & params$JoinJunc==FALSE) {
  Peaksdata3_anno=Peaksdata2_anno[,c("ID",'chr',"start","end","strand",
                                     'Counts_Unique','Counts_fracMM',
                                     "Same_gene_name_comb","Same_ensembl_gene_id","Same_type_comb",
                                     "Same_Repeat_comb",'Same_feature',"Same_Comb_type_exon",
                                     "Same_Comb_type_ncRNA","Oppo_gene_name_comb",
                                     "Oppo_ensembl_gene_id","Oppo_type_comb","Oppo_Repeat_comb",
                                     'Oppo_feature',"Oppo_Comb_type_exon","Oppo_Comb_type_ncRNA",
                                     "Comb_type_exon_Oppo")]
  colnames(Peaksdata3_anno)=c("ID",'chr',"start","end","strand",'Counts_Unique',
                            'Counts_Multimappers_Scaled',"Same Strand: Host_gene_name",
                            "Same Strand: Host_gene_ensembl_id","Same Strand: RNA_type",
                            'Same Strand: Repeat_Type',"Same Strand: Intron Exon",
                            'Same Strand: RNA_type_Classification','Same Strand: ncRNA_Classification',
                            "Opposite Strand: Host_gene_name",
                            "Opposite Strand: Host_gene_ensembl_id","Opposite Strand: RNA_type",
                            'Opposite Strand: Repeat_Type',"Opposite Strand: Intron Exon",
                            'Opposite Strand: RNA_type_Classification',
                            'Opposite Strand: ncRNA_Classification',
                            'Both Strand: RNA_type_Classification')
}else if (params$Condense==TRUE|params$JoinJunc==TRUE) {
  Peaksdata3_anno=Peaksdata2_anno[,c("ID","IDmerge",'chr',"start","end","strand",'Counts_Unique',
                                   'Counts_fracMM',"Same_gene_name_comb","Same_ensembl_gene_id",
                                   "Same_type_comb","Same_Repeat_comb",'Same_feature',
                                   "Same_Comb_type_exon",
                                   "Same_Comb_type_ncRNA","Oppo_gene_name_comb",
                                   "Oppo_ensembl_gene_id","Oppo_type_comb",
                                   "Oppo_Repeat_comb",'Oppo_feature',
                                   "Oppo_Comb_type_exon","Oppo_Comb_type_ncRNA","Comb_type_exon_Oppo")]
  colnames(Peaksdata3_anno)=c("ID","IDmerge",'chr',"start","end","strand",
                              'Counts_Unique','Counts_Multimappers_Scaled',
                              "Same Strand: Host_gene_name","Same Strand: Host_gene_ensembl_id",
                              "Same Strand: RNA_type",'Same Strand: Repeat_Type',
                              "Same Strand: Intron Exon",'Same Strand: RNA_type_Classification',
                              'Same Strand: ncRNA_Classification',
                              "Opposite Strand: Host_gene_name",
                              "Opposite Strand: Host_gene_ensembl_id",
                              "Opposite Strand: RNA_type",'Opposite Strand: Repeat_Type',
                              "Opposite Strand: Intron Exon",
                              'Opposite Strand: RNA_type_Classification',
                              'Opposite Strand: ncRNA_Classification',
                              'Both Strand: RNA_type_Classification')
}
Peaksdata4=Peaksdata3_anno
```

<br>  

# Output Data  
<!-- <br>   -->
<!-- Location:   -->
<!-- smb://at-s-is2.ncifcrf.gov/rbl-fs/mESC_clip/Novoalign_Spliced/    -->
<!-- <br>   -->

```{r ,fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=T,include=F}
write.table(Peaksdata4,file=paste0(params$OutDIR,samplename,"_CLIP_",params$PeakIdnt,"Peaks",ntmerge,'_peakDepth',params$readdepth,params$NameAdd,"_MD15.txt"), sep = "\t", row.names = FALSE, col.names = T, append = F, quote= FALSE,na = "")
```

### fix this is hardcoded for WT and KO
```{r ,fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,include=F}
#RUN2
###CTK
WT_Peaks=fread(paste0("WT_CLIP_",params$PeakIdnt,"Peaks",ntmerge,'_peakDepth',params$readdepth,params$NameAdd,"_SpliceAware_MD15.txt"), header=T, sep="\t",stringsAsFactors = F,data.table=F)

WT_Peaks$start=as.numeric(WT_Peaks$start);WT_Peaks$end=as.numeric(WT_Peaks$end)

WT_Peaks.GR <- GRanges(seqnames = as.character(WT_Peaks$chr), ranges=IRanges(start = as.numeric(WT_Peaks$start), end = as.numeric(WT_Peaks$end)),strand = WT_Peaks$strand,ID=WT_Peaks$ID )

##########################

RoKO_Peaks=fread(paste0("RoKO_CLIP_",params$PeakIdnt,"Peaks",ntmerge,'_peakDepth',params$readdepth,params$NameAdd,"_MD15.txt"), header=T, sep="\t",stringsAsFactors = F,data.table=F)

RoKO_Peaks$start=as.numeric(RoKO_Peaks$start);RoKO_Peaks$end=as.numeric(RoKO_Peaks$end)

RoKO_Peaks.GR <- GRanges(seqnames = as.character(RoKO_Peaks$chr), ranges=IRanges(start = as.numeric(RoKO_Peaks$start), end = as.numeric(RoKO_Peaks$end)),strand = RoKO_Peaks$strand,ID=RoKO_Peaks$ID )

##########################
RoKO_ctk=fread(paste0("./peaks_ctk/RoKO/RoKO_Clip_iCountcutadpt_all.unique.NH.mm.ddup.unique.sig00.peakcount.boundary.bed"), header=T, sep="\t",stringsAsFactors = F,data.table=F)
colnames(RoKO_ctk)=c('chr','start','end','anno','count','strand')
RoKO_ctk=separate(RoKO_ctk,anno,sep='\\]\\[',into=c('CDKpeak','PH','PH0','Pval'))
RoKO_ctk$PH=gsub("PH=","",RoKO_ctk$PH);RoKO_ctk$PH=as.numeric(RoKO_ctk$PH)
RoKO_ctk$PH0=gsub("PH0=","",RoKO_ctk$PH0);RoKO_ctk$PH0=as.numeric(RoKO_ctk$PH0)
RoKO_ctk$Pval=gsub("P=","",RoKO_ctk$Pval);RoKO_ctk$Pval=gsub("\\]","",RoKO_ctk$Pval);RoKO_ctk$Pval=as.numeric(RoKO_ctk$Pval)
RoKO_ctk=RoKO_ctk[RoKO_ctk$count>=5,]

q = WT_Peaks.GR
s = RoKO_Peaks.GR
xo=(GenomicRanges::findOverlaps(q,s,type = "any",ignore.strand=F))

sh=as.data.frame(s[subjectHits(xo)]);colnames(sh)=paste0(colnames(sh),'_RoKO')
qh=as.data.frame(q[queryHits(xo)]);colnames(qh)=paste0(colnames(qh),'_WT')
overlaps <- as.data.frame(pintersect(q[queryHits(xo)], s[subjectHits(xo)]))
shqh= cbind(sh,qh,overlaps)

shqh$percentOverlap <- shqh$width / rowMin(as.matrix(shqh[,c('width_RoKO','width_WT')]))
shqh=shqh[shqh$percentOverlap>.5,]  

WT_Peaks_Shared=merge(WT_Peaks,shqh[,c('ID_WT','ID_RoKO')],by.x='ID',by.y='ID_WT')
WT_Peaks_Shared=merge(WT_Peaks_Shared,RoKO_Peaks[,c('ID','Counts_Unique')],by.x='ID_RoKO',by.y='ID',suffixes=c("","_RoKO"))


wtdup=unique(WT_Peaks_Shared[duplicated(WT_Peaks_Shared$ID),'ID'])
wtdupall=WT_Peaks_Shared[WT_Peaks_Shared$ID%in%wtdup,]
wtdupall=separate(wtdupall,col = ID_RoKO,into = c('chr_RoKO','start_RoKO'),sep = ':',remove = F)
wtdupall=separate(wtdupall,col = start_RoKO,into = c('start_RoKO','end_RoKO'),sep = '-',remove = F)
wtdupall$start_RoKO=as.numeric(wtdupall$start_RoKO);wtdupall$end_RoKO=as.numeric(wtdupall$end_RoKO)

wtdupall_out=as.data.frame(matrix(nrow=length(wtdup),ncol = ncol(wtdupall)));colnames(wtdupall_out)=colnames(wtdupall)
wtdupall_out$ID_RoKO_comb=NA
wtdupall_out$Counts_Unique_RoKO_Comb=NA
for (x in 1:length(wtdup)) {
  l=wtdupall[wtdupall$ID%in%wtdup[x],]
  wtdupall_out[x,]=l[1,]
  wtdupall_out[x,'ID_RoKO_comb']=paste0(l[1,'chr_RoKO'],':',min(l$start_RoKO),'-',max(l$end_RoKO))
  wtdupall_out[x,'Counts_Unique_RoKO_Comb']=sum(l$Counts_Unique_RoKO)
}
wtdupall_out$Counts_Unique_RoKO_Comb=as.numeric(wtdupall_out$Counts_Unique_RoKO_Comb)

WT_Peaks_Shared=merge(WT_Peaks_Shared,wtdupall_out[,c('ID','ID_RoKO_comb','Counts_Unique_RoKO_Comb')],by='ID',all.x=T)

WT_Peaks_Shared=WT_Peaks_Shared[,c("ID","ID_RoKO",'ID_RoKO_comb' ,"strand", "Counts_Unique","Counts_Unique_RoKO",'Counts_Unique_RoKO_Comb',"Counts_All","Counts_Multimappers_Scaled" , "Counts_Multimappers_BestMapping","Multimaped Reads %","Same Strand: Host_gene_name", "Same Strand: Host_gene_ensembl_id","Same Strand: RNA_type","Same Strand: Repeat_Type", "Same Strand: Intron Exon","Same Strand: RNA_type_Classification","Same Strand: ncRNA_Classification", "Opposite Strand: Host_gene_name","Opposite Strand: Host_gene_ensembl_id","Opposite Strand: RNA_type", "Opposite Strand: Repeat_Type","Opposite Strand: Intron Exon","Opposite Strand: RNA_type_Classification", "Opposite Strand: ncRNA_Classification","Both Strand: RNA_type_Classification","MM_number", "MM_Alt_Peaktype","MM_Same_Peaktype","MM_type", "MM_Prec_Alt_Peaktype","MM_Alt_Alignments")]


write.table(WT_Peaks_Shared,file=paste0(params$OutDIR,samplename,"sharedCLIP_",params$PeakIdnt,"Peaks",ntmerge,'_peakDepth',params$readdepth,params$NameAdd,"_MD15.txt"), sep = "\t", row.names = FALSE, col.names = T, append = F, quote= FALSE,na = "")

WT_Peaks_unique=WT_Peaks[(WT_Peaks$ID%in%WT_Peaks_Shared$ID)==F,]

write.table(WT_Peaks_unique,file=paste0(params$OutDIR,samplename,"uniqueCLIP_",params$PeakIdnt,"Peaks",ntmerge,'_peakDepth',params$readdepth,params$NameAdd,"_MD15.txt"), sep = "\t", row.names = FALSE, col.names = T, append = F, quote= FALSE,na = "")
```

## Counts Table : 

"`r paste0(samplename,"_CLIP_",params$PeakIdnt,"Peaks",ntmerge,'_peakDepth',params$readdepth,params$NameAdd,"_MD15.txt")`"  

**Columns:**  
"ID" - CLIP peak location  
"strand" - CLIP peak stand  
<!-- "Average MAPQ" - Average Mapping quality of reads aligned to peak region.   -->
"Counts_Unique" - Number of Unique reads aligned to CLIP peak  
<!-- "Counts_All" - Count of Multimapped reads for each peak     -->
<!-- "Counts_All" - Count of Unique + Multimapped read for each peak (Each occurrence of Multimapped read is counted separately)   -->
"Counts_Multimappers_Scaled"  - number of reads with Unique reads =1 and Multimapped =1/#MM locations  
<!-- "Counts_Multimappers_Best Mapping" - Number of Unique reads + best mapQ Multimapped Read aligned to CLIP peak   -->
<!-- "Multimaped Reads %" - Percent of Multimapped reads that align to CLIP peak   -->
<!-- "Pvalue" - Sample specific peak P-Value compared to Control - MAnorm.   -->
<!-- "WT-Normalized count"- Normalized Peak count generated by MAnorm.   -->
<!-- "RoKO-Normalized count"- Control Sample normalized Peak count generated by MAnorm.   -->
<!-- "FC" - Log2 Fold Change (WT-RoKO) using MAnorm normalized counts.    -->
  
"Same Strand: Host_gene_name" - Name of Host Gene on same strand as CLIP reads  
"Same Strand: Host_gene_ensembl_id" - Ensemble Name of Host Gene on same strand as CLIP reads  
"Same Strand: RNA_type" - Transcript type of CLIP peak host gene on same strand as CLIP reads  
"Same Strand: Repeat_Type" - Type of repeat in Clip peak (determined by repeat masker) on same strand as CLIP reads  
"Same Strand: Intron Exon" - Gene feature of CLIP peak location in protein coding Gene on same strand as CLIP reads  
"Same Strand: RNA_type_Classification" - Summary of Peak Classification   
"Same Strand: ncRNA_Classification" - Summary of ncRNA Peak assignments  

"Opposite Strand: Host_gene_name" - Name of Host Gene on opposite strand as CLIP reads  
"Opposite Strand: Host_gene_ensembl_id" - Ensemble Name of Host Gene on opposite strand as CLIP reads  
"Opposite Strand: RNA_type" - Transcript type of CLIP peak host gene on opposite strand as CLIP reads  
"Opposite Strand: Repeat_Type" - Type of repeat in Clip peak (determined by repeat masker) on opposite strand as CLIP reads  
"Opposite Strand: Intron Exon" - Gene feature of CLIP peak location in protein coding Gene on opposite strand as CLIP reads  
"Opposite Strand: RNA_type_Classification" - Summary of Peak Classification  
"Opposite Strand: ncRNA_Classification" - Summary of ncRNA Peak assignments  

"Both Strand: RNA_type_Classification" - Summary of Peak Classification including both strand annotations  
<!-- "MM_number" - # of reads in CLIP peak that aligns to other locations Genome   -->
<!-- "MM_Alt_Peaktype" - # of Multimapped reads with Alternative Peak Classifications different from original Peak Classification   -->
<!-- "MM_Same_Peaktype" - # of Multimapped reads with the same Peak Classification as the original Peak Classification   -->
<!-- "MM_type" - Peak Classifications for alternative mappings of multimapped reads   -->
<!-- "MM_Prec_Alt_Peaktype" - % of Multimapped reads with Alternative Peak Classifications different from original Peak Classification   -->
<!-- "MM_Alt_Alignments" - Location alternate alignments for Multimapped reads   -->

<!-- "iCount_peak" - 1= peak is identified by iCount -->
<br>



<!-- ## Alignment Tracks   -->

<!-- `r toString(samplename)`_Clip_iCountcutadpt_all.unique.NH.mm.ddup.bam - MultiMapped + Uniquely aligned CLIP Reads   -->
<!-- `r toString(samplename)`_Clip_iCountcutadpt_all.unique.NH.mm.ddup.unique.bam - Uniquely aligned CLIP Reads   -->
<!-- `r toString(samplename)`_Clip_iCountcutadpt_all.unique.NH.mm.ddup.multimapped.bam - MultiMapped aligned CLIP Reads   -->

<br>
<br>

<!-- ## Annotation Tracks     -->

<!-- sftp://Biowulf.nih.gov/data/RBL_NCI/datashare/wolin/mESC_Clip/annotation_files/ -->


<!-- <br>   -->
<!-- <br>   -->

<!-- ## Compare MM peaks alignment to Unique Peaks -->

<!-- <br> -->

<!-- ```{r ,fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=T,include=F} -->
<!-- colmns=c('chr','start','end','ID',"Counts_Multimappers",'strand',"Counts_Unique","Counts_Multimappers_Scaled",'Both Strand: RNA_type_Classification','Same Strand: ncRNA_Classification') -->


<!-- UniqPeaks_Peaks=fread(paste0(samplename,"_CLIP_UniquePeaks",ntmerge,'_peakDepth',params$readdepth,params$NameAdd,"_MD15.txt"), header=T, sep="\t",stringsAsFactors = F,data.table=F) -->
<!-- # UniqPeaks_Peaks=separate(UniqPeaks_Peaks,ID,into = c('chr','start','end'),sep = ":|-",remove = F) -->
<!-- # UniqPeaks_Peaks$start=as.numeric(UniqPeaks_Peaks$start) -->
<!-- # UniqPeaks_Peaks$end=as.numeric(UniqPeaks_Peaks$end) -->
<!-- UniqPeaks_Peaks[(UniqPeaks_Peaks$`Same Strand: ncRNA_Classification`)%in%"",'Same Strand: ncRNA_Classification']="NA" -->
<!--     write.table(UniqPeaks_Peaks[,colmns],file=("./test/UniqPeaks_Peaks.bed"), sep = "\t", row.names = FALSE, col.names = F, append = F, quote= FALSE) -->


<!-- MMpeaks_Peaks=fread(paste0(samplename,"_CLIP_MultiMapPeaks",ntmerge,'_peakDepth',params$readdepth,params$NameAdd,"_MD15.txt"), header=T, sep="\t",stringsAsFactors = F,data.table=F) -->
<!-- # MMpeaks_Peaks=separate(MMpeaks_Peaks,ID,into = c('chr','start','end'),sep = ":|-",remove = F) -->
<!-- # MMpeaks_Peaks$start=as.numeric(MMpeaks_Peaks$start) -->
<!-- # MMpeaks_Peaks$end=as.numeric(MMpeaks_Peaks$end) -->
<!-- MMpeaks_Peaks[(MMpeaks_Peaks$`Same Strand: ncRNA_Classification`)%in%"",'Same Strand: ncRNA_Classification']="NA" -->
<!--     write.table(MMpeaks_Peaks[,colmns],file=("./test/MMpeaks_Peaks.bed"), sep = "\t", row.names = FALSE, col.names = F, append = F, quote= FALSE) -->



<!-- allpeaks_Peaks=fread(paste0(samplename,"_CLIP_allPeaks",ntmerge,'_peakDepth',params$readdepth,params$NameAdd,"_MD15.txt"), header=T, sep="\t",stringsAsFactors = F,data.table=F) -->
<!-- # allpeaks_Peaks=separate(allpeaks_Peaks,ID,into = c('chr','start','end'),sep = ":|-",remove = F) -->
<!-- # allpeaks_Peaks$start=as.numeric(allpeaks_Peaks$start) -->
<!-- # allpeaks_Peaks$end=as.numeric(allpeaks_Peaks$end) -->
<!-- allpeaks_Peaks[(allpeaks_Peaks$`Same Strand: ncRNA_Classification`)%in%"",'Same Strand: ncRNA_Classification']="NA" -->
<!--     write.table(allpeaks_Peaks[,colmns],file=("./test/allpeaks_Peaks.bed"), sep = "\t", row.names = FALSE, col.names = F, append = F, quote= FALSE) -->


<!-- ############################################################################################################################################################################################################################################################## -->
<!-- ``` -->


<!-- ```{r ,fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=T,include=F} -->
<!-- setA=allpeaks_Peaks -->
<!-- setB=UniqPeaks_Peaks -->
<!-- setAname='Allpeaks' -->
<!-- setBname='UniqPeaks' -->
<!-- setAbed='allpeaks_Peaks.bed' -->
<!-- setBbed='UniqPeaks_Peaks.bed' -->

<!-- setAcount=paste0(setAname,"_Counts_Unique") -->
<!-- setBcount=paste0(setBname,"_Counts_Unique") -->


<!-- nc_color=c("#1B9E77","#1fb487", -->
<!--            "#2bdba6" , -->
  <!--            "#D95F02", "#7570B3" ,"#E7298A", "#66A61E", "#E6AB02", "#A6761D", "#666666") -->
  
  
  <!-- # MMpeaks_OL->SetApeaks_OL -->
  <!-- # SetApeaksSetBpeaks_All -> SetApeaksSetBpeaks_All -->
  <!-- # UniqPeaks_Only -> setBPeaks_Only -->
  <!-- # MMpeaks_Only -> setApeaks_Only -->
  
  <!--  system(paste0('bedtools intersect -split -a ./test/',setAbed,' -b ./test/',setBbed,' -wao -s >./test/',setAname,'_OL.txt')) -->
  <!--     MMpeaks_OL=fread(paste0("./test/",setAname,"_OL.txt"), header=F, sep="\t",stringsAsFactors = F,data.table=F) -->
    <!--     colnames(MMpeaks_OL)=c(paste0(setAname,'_',colmns),paste0(setBname,'_',colmns),'NTOL') -->
      
      
      <!-- MMpeaks_OL[,setAcount]=as.numeric(MMpeaks_OL[,setAcount]) -->
        <!-- MMpeaks_OL[,setBcount]=as.numeric(MMpeaks_OL[,setBcount]) -->
          <!-- MMpeaks_OL[,paste0(setAname,c('_Both Strand: RNA_type_Classification'))]=factor(MMpeaks_OL[,paste0(setAname,c('_Both Strand: RNA_type_Classification'))], levels = c("ncRNA", "protein_coding: exon", "Repeat Element","pseudogene","lncRNA-exon","Antisense Feature","protein_coding: Intron","lncRNA-intron","lncRNA","no Feature")) -->
            
            
            
            <!-- ################################################## -->
            
            <!-- system(paste0('bedtools intersect -split -a ./test/',setBbed,' -b ./test/',setAbed,' -wao -s >./test/',setBname,'_OL.txt')) -->
            <!--     setB_OL=fread(paste0("./test/",setBname,"_OL.txt"), header=F, sep="\t",stringsAsFactors = F,data.table=F) -->
              <!--     colnames(setB_OL)=c(paste0(setBname,'_',colmns),paste0(setAname,'_',colmns),'NTOL') -->
                
                
                <!-- setB_OL[,setAcount]=as.numeric(setB_OL[,setAcount]) -->
                  <!-- setB_OL[,setBcount]=as.numeric(setB_OL[,setBcount]) -->
                    <!-- setB_OL[,paste0(setAname,c('_Both Strand: RNA_type_Classification'))]=factor(setB_OL[,paste0(setAname,c('_Both Strand: RNA_type_Classification'))], levels = c("ncRNA", "protein_coding: exon", "Repeat Element","pseudogene","lncRNA-exon","Antisense Feature","protein_coding: Intron","lncRNA-intron","lncRNA","no Feature")) -->
                      
                      
                      
                      
                      <!-- setApeaks_Only=MMpeaks_OL[MMpeaks_OL[,(paste0(setBname,'_Counts_Multimappers_Scaled'))]%in%".",] -->
                        <!-- setBPeaks_Only=setB_OL[setB_OL[,(paste0(setAname,'_Counts_Multimappers_Scaled'))]%in%".",] -->
                          
                          <!-- SetApeaksSetBpeaks_All=(rbind(MMpeaks_OL,setBPeaks_Only)) -->
                            
                            <!-- setAPeaks_All=SetApeaksSetBpeaks_All[SetApeaksSetBpeaks_All[,paste0(setAname,'_ID')]%in%"."==F,] -->
                              <!-- setBPeaks_All=SetApeaksSetBpeaks_All[SetApeaksSetBpeaks_All[,paste0(setBname,'_ID')]%in%"."==F,] -->
                                <!-- SetApeaksSetBpeaks=SetApeaksSetBpeaks_All[SetApeaksSetBpeaks_All[,paste0(setAname,'_ID')]%in%"."==F& -->
                                                                                 <!--                                         SetApeaksSetBpeaks_All[,paste0(setBname,'_ID')]%in%"."==F  ,] -->
                                  
                                  
                                  <!-- ``` -->
                                  
                                  
                                  <!-- ```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=T,incude=T} -->
                                  
                                  <!-- #echo=F, include=T, eval=T, fig.align='default', fig.ncol=2, fig.height=3.5, fig.width=7, out.height=200, out.width="50%", fig.show="hold", layout='l-screen', results = FALSE, message=FALSE , warning=F -->
                                  
                                  <!-- xx=(paste0(setAname,'_Counts_Multimappers_Scaled')) -->
                                    <!-- yy=(paste0(setBname,'_Counts_Multimappers_Scaled')) -->
                                      <!-- plt=MMpeaks_OL -->
                                        <!--     plt[,xx]=as.numeric(plt[,xx]) -->
                                          <!--     plt[,yy]=as.numeric(plt[,yy]) -->
                                            <!--     # plt=plt[is.na(plt[,yy])==F,] -->
                                            <!-- colnames(plt)[colnames(plt)%in%paste0(setBname,'_Both Strand: RNA_type_Classification')]=paste0(setBname,'_BothStrand_RNA_type_Classification') -->
                                              <!-- colr=paste0(setBname,'_BothStrand_RNA_type_Classification') -->
                                                <!-- p=ggplot(plt,aes_string(x=xx,y=yy,color=colr#, -->
                                                                             <!--                            # text=paste0('MMpeaks ID: ',MMpeaks_ID,'\nNo MMpeaks ID: ',UniqPeaks_ID, -->
                                                                               <!--                            #              '\n MMpeaks Classification: ', `MMpeaks_Both Strand: RNA_type_Classification`, -->
                                                                               <!--                            #              '\n No MMpeaks Classification: ', `UniqPeaks_Both Strand: RNA_type_Classification`, -->
                                                                               <!--                            #              '\n MMpeaks ncRNA Classification: ', `MMpeaks_Same Strand: ncRNA_Classification`, -->
                                                                               <!--                            #              '\n No MMpeaks ncRNA Classification: ', `UniqPeaks_Same Strand: ncRNA_Classification`) -->
                                                                               <!--                          ))+ -->
                                                  <!--   geom_point(size=1)+scale_x_continuous(trans = "log2") +scale_y_continuous(trans = "log2")+ -->
                                                  <!--   theme_classic()+scale_color_brewer(palette = "Dark2") -->
                                                  <!-- ggplotly(p) -->
                                                  
                                                  <!-- ################################################## -->
                                                  
                                                  
                                                  <!-- # system('bedtools intersect -split -a ./test/UniqPeaks_Peaks.bed -b ./test/MMpeaks_Peaks.bed -wao -s >./test/UniqPeakspeaks_mm10_OL.txt') -->
                                                  <!-- #     UniqPeaks_OL=fread(paste0("./test/UniqPeakspeaks_mm10_OL.txt"), header=F, sep="\t",stringsAsFactors = F,data.table=F) -->
                                                  <!-- #     colnames(UniqPeaks_OL)=c(paste0('UniqPeaks_',colmns),paste0('MMpeaks_',colmns),'NTOL') -->
                                                  <!-- #     UniqPeaks_OL$MMpeaks_Counts_Unique=as.numeric(UniqPeaks_OL$MMpeaks_Counts_Unique) -->
                                                  <!-- # UniqPeaks_OL[,'MMpeaks_Both Strand: RNA_type_Classification']=factor(UniqPeaks_OL[,'MMpeaks_Both Strand: RNA_type_Classification'], levels = c("ncRNA", "protein_coding: exon", "Repeat Element","pseudogene","lncRNA-exon","Antisense Feature","protein_coding: Intron","lncRNA-intron","lncRNA","no Feature")) -->
                                                  <!-- # UniqPeaks_OL[,'UniqPeaks_Both Strand: RNA_type_Classification']=factor(UniqPeaks_OL[,'UniqPeaks_Both Strand: RNA_type_Classification'], levels = c("ncRNA", "protein_coding: exon", "Repeat Element","pseudogene","lncRNA-exon","Antisense Feature","protein_coding: Intron","lncRNA-intron","lncRNA","no Feature")) -->
                                                  
                                                  
                                                  <!-- # p=ggplot(UniqPeaks_OL,aes(x=UniqPeaks_Counts_Unique,y=MMpeaks_Counts_Unique,color=`MMpeaks_Both Strand: RNA_type_Classification`, -->
                                                  <!-- #                            text=paste0('MMpeaks ID: ',MMpeaks_ID,'\nNo MMpeaks ID: ',UniqPeaks_ID, -->
                                                  <!-- #                                         '\n MMpeaks Classification: ', `MMpeaks_Both Strand: RNA_type_Classification`, -->
                                                  <!-- #                                         '\n No MMpeaks Classification: ', `UniqPeaks_Both Strand: RNA_type_Classification`, -->
                                                  <!-- #                                         '\n MMpeaks ncRNA Classification: ', `MMpeaks_Same Strand: ncRNA_Classification`, -->
                                                  <!-- #                                         '\n No MMpeaks ncRNA Classification: ', `UniqPeaks_Same Strand: ncRNA_Classification`) -->
                                                  <!-- #                          ))+geom_point(size=1)+scale_x_continuous(trans = "log2") +scale_y_continuous(trans = "log2")+theme_classic()+scale_color_brewer(palette = "Dark2") -->
                                                  <!-- # ggplotly(p) -->
                                                  
                                                  
                                                  <!-- # nrow(UniqPeaks_OL[UniqPeaks_OL$MMpeaks_ID%in%"."==F,]) -->
                                                  <!-- # nrow(MMpeaks_OL[MMpeaks_OL$UniqPeaks_ID%in%"."==F,]) -->
                                                  
                                                  <!-- ##### Venn Diagram -->
                                                  
                                                  <!-- c3=as.data.frame(unique(c(MMpeaks_OL[,paste0(setAname,'_ID')],setBPeaks_Only[,paste0(setBname,'_ID')]))) -->
                                                    <!-- c3[,paste0(setAname)]=c3[,1]%in%setAPeaks_All[,paste0(setAname,'_ID')] -->
                                                      <!-- c3[,paste0(setBname)]=c3[,1]%in%setBPeaks_All[,paste0(setAname,'_ID')] -->
                                                        <!-- # c3[c3[,1]%in%setBPeaks_Only[,paste0(setBname,'_ID')],paste0(setBname)]=TRUE -->
                                                        <!-- c3=c3[,c(paste0(setAname),paste0(setBname))] -->
                                                          <!-- c3=vennCounts(c3) -->
                                                            <!-- vennDiagram(c3,circle.col=c('red','blue'),lwd=2) -->
                                                            
                                                            
                                                            <!-- # ###### side by side Column -->
                                                            <!-- # -->
                                                            <!-- # -->
                                                            <!-- # MMpeaks_cat_count=(count(SetApeaksSetBpeaks_All$`MMpeaks_Both Strand: RNA_type_Classification`)) -->
                                                            <!-- #   colnames(MMpeaks_cat_count)=c('Catagory','Count') -->
                                                            <!-- #     MMpeaks_cat_count=MMpeaks_cat_count[is.na(MMpeaks_cat_count[,1])==F,] -->
                                                            <!-- # -->
                                                            <!-- # UniqPeaks_cat_count=(count(SetApeaksSetBpeaks_All$`UniqPeaks_Both Strand: RNA_type_Classification`)) -->
                                                            <!-- #   colnames(UniqPeaks_cat_count)=c('Catagory','Count') -->
                                                            <!-- #     UniqPeaks_cat_count=UniqPeaks_cat_count[UniqPeaks_cat_count[,1]%in%"."==F,] -->
                                                            <!-- # -->
                                                            <!-- # -->
                                                            <!-- # MMpeaks_cat_count$Sample='MMpeaks Aware'; -->
                                                            <!-- # MMpeaks_cat_count$frequency=(MMpeaks_cat_count$Count/(sum(MMpeaks_cat_count$Count)))*100 -->
                                                            <!-- # UniqPeaks_cat_count$Sample='No MMpeaks'; -->
                                                            <!-- # UniqPeaks_cat_count$frequency=(UniqPeaks_cat_count$Count/(sum(UniqPeaks_cat_count$Count)))*100 -->
                                                            <!-- # -->
                                                            <!-- # CatCompare=rbind(MMpeaks_cat_count,UniqPeaks_cat_count); -->
                                                            <!-- # CatCompare[,'Sample']=factor(CatCompare[,'Sample'], levels = c('MMpeaks Aware', 'No MMpeaks')) -->
                                                            <!-- # -->
                                                            <!-- # -->
                                                            <!-- # ggplot((CatCompare),aes(Catagory,Count,fill=Sample)) + geom_bar(stat = "identity", position = 'dodge')+ -->
                                                            <!-- # theme(axis.text.x = element_text(angle = 45, hjust = 1))+theme_classic() -->
                                                            
                                                            
                                                            <!-- # ggplot((CatCompare),aes(Catagory,frequency,fill=Sample)) + geom_bar(stat = "identity", position = 'dodge')+ -->
                                                            <!-- # theme(axis.text.x = element_text(angle = 45, hjust = 1))+theme_classic() -->
                                                            
                                                            
                                                            <!-- ######################################################## -->
                                                            <!-- #### MMpeaks Only -->
                                                            <!-- ######################################################## -->
                                                            <!-- # count(setApeaks_Only$`MMpeaks_Both Strand: RNA_type_Classification`) -->
                                                            
                                                            <!-- MMpeaksOnly_cat_count=(count(setApeaks_Only[,paste0(setAname,'_Both Strand: RNA_type_Classification')])) -->
                                                              <!--   colnames(MMpeaksOnly_cat_count)=c('Catagory','Count') -->
                                                                <!--     MMpeaksOnly_cat_count=MMpeaksOnly_cat_count[is.na(MMpeaksOnly_cat_count[,1])==F,] -->
                                                                  <!-- MMpeaksOnly_cat_count[,'Catagory']=factor(MMpeaksOnly_cat_count[,'Catagory'], levels = c("ncRNA", "protein_coding: exon", "Repeat Element","pseudogene","lncRNA-exon","Antisense Feature","protein_coding: Intron","lncRNA-intron","lncRNA","no Feature")) -->
                                                                    
                                                                    <!-- write.table(setApeaks_Only,file=paste0(samplename,"_CLIP_",params$PeakIdnt,"Peaks",ntmerge,'_peakDepth',params$readdepth,params$NameAdd,"_MMpeaksAwareOnly_MD15.txt"), sep = "\t", row.names = FALSE, col.names = T, append = F, quote= FALSE,na = "") -->
                                                                    
                                                                    
                                                                    <!-- ######################################################## -->
                                                                    <!-- #### UniqPeaks Only -->
                                                                    <!-- ######################################################## -->
                                                                    <!-- # UniqPeaksOnly_cat_count=(count(UniqPeaks_Only$`UniqPeaks_Both Strand: RNA_type_Classification`)) -->
                                                                    <!-- #   colnames(UniqPeaksOnly_cat_count)=c('Catagory','Count') -->
                                                                    <!-- #     UniqPeaksOnly_cat_count=UniqPeaksOnly_cat_count[is.na(UniqPeaksOnly_cat_count[,1])==F,] -->
                                                                    <!-- # UniqPeaksOnly_cat_count[,'Catagory']=factor(UniqPeaksOnly_cat_count[,'Catagory'], levels = c("ncRNA", "protein_coding: exon", "Repeat Element","pseudogene","lncRNA-exon","Antisense Feature","protein_coding: Intron","lncRNA-intron","lncRNA","no Feature")) -->
                                                                    <!-- #  -->
                                                                    <!-- #  -->
                                                                    <!-- # write.table(UniqPeaks_Only,file=paste0(samplename,"_CLIP_",params$PeakIdnt,"Peaks",ntmerge,'_peakDepth',params$readdepth,params$NameAdd,"_NoSplicingOnly_MD15.txt"), sep = "\t", row.names = FALSE, col.names = T, append = F, quote= FALSE,na = "") -->
                                                                    
                                                                    
                                                                    
                                                                    
                                                                    <!-- ``` -->
                                                                    
                                                                    <!-- <br>    -->
                                                                    
                                                                    <!-- #### Counts Identified using All Reads only      -->
                                                                    
                                                                    
                                                                    <!-- <br> -->
                                                                    <!-- ```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=T,incude=F} -->
                                                                    
                                                                    <!-- ######## -->
                                                                    <!-- # MMpeaksOnly_cat_count=rbind(MMpeaksOnly_cat_count,c("pseudogene",0)) -->
                                                                    <!-- # MMpeaksOnly_cat_count$Count=as.numeric(MMpeaksOnly_cat_count$Count) -->
                                                                    <!-- # MMpeaksOnly_cat_count$Transcript="" -->
                                                                    <!-- # gg=ggplot(MMpeaksOnly_cat_count,aes(fill=Catagory,x=Transcript,y=Count) )+geom_bar(stat = "identity",position="stack",width=.5)+theme_classic()+ggtitle("Number of peaks only Idnetified by \nAll Peaks")+ -->
                                                                    <!-- # # theme(plot.title = element_text(hjust = 0.5,size = 25),axis.title=element_text(size=20),axis.text=element_text(size=15),legend.text = element_text( size=30))+ -->
                                                                    <!-- #  scale_fill_brewer(palette = "Dark2") -->
                                                                    <!-- # ggplotly(gg) -->
                                                                    
                                                                    
                                                                    
                                                                    <!-- MMpeaksOnly_cat_count=rbind(MMpeaksOnly_cat_count,c("pseudogene",0)) -->
                                                                      <!-- MMpeaksOnly_cat_count$Count=as.numeric(MMpeaksOnly_cat_count$Count) -->
                                                                        <!-- MMpeaksOnly_cat_count$Transcript="" -->
                                                                          <!-- gg=ggplot(MMpeaksOnly_cat_count,aes(fill=Catagory,x=Transcript,y=Count) )+geom_bar(stat = "identity",position="stack",width=.5)+theme_classic()+ggtitle("Number of peaks only Idnetified by \nAll Peaks")+ -->
                                                                            <!-- # theme(plot.title = element_text(hjust = 0.5,size = 25),axis.title=element_text(size=20),axis.text=element_text(size=15),legend.text = element_text( size=30))+ -->
                                                                            <!--  scale_fill_brewer(palette = "Dark2") -->
                                                                            <!-- ggplotly(gg) -->
                                                                            
                                                                            
                                                                            <!-- # UniqPeaksOnly_cat_count$Transcript="" -->
                                                                            <!-- # gg=ggplot(UniqPeaksOnly_cat_count,aes(fill=Catagory,x=Transcript,y=Count) )+geom_bar(stat = "identity",position="stack",width=.5)+theme_classic()+ggtitle("Number of peaks only Idnetified with \n Uniquepeaks")+ -->
                                                                            <!-- # # theme(plot.title = element_text(hjust = 0.5,size = 25),axis.title=element_text(size=20),axis.text=element_text(size=15),legend.text = element_text( size=30))+ -->
                                                                            <!-- #  scale_fill_brewer(palette = "Dark2") -->
                                                                            <!-- # ggplotly(gg) -->
                                                                            
                                                                            
                                                                            
                                                                            
                                                                            <!-- p=setApeaks_Only -->
                                                                              <!-- p$Same_Comb_type_exon=p$`Allpeaks_Both Strand: RNA_type_Classification` -->
                                                                                <!--   # if (incd_rRNA==F) { -->
                                                                                <!-- #   p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA')) -->
                                                                                <!-- # } -->
                                                                                <!-- # p$all=as.character(p$`Allpeaks_Both Strand: RNA_type_Classification`) -->
                                                                                <!-- # p[p$`Allpeaks_Same Strand: ncRNA_Classification`%in%'rRNA','Allpeaks_Both Strand: RNA_type_Classification']='rRNA' -->
                                                                                <!-- # p[p$`Allpeaks_Same Strand: ncRNA_Classification`%in%'yRNA','Allpeaks_Both Strand: RNA_type_Classification']='yRNA' -->
                                                                                <!-- #  -->
                                                                                <!-- # p$Same_Comb_type_exon=factor(p$Same_Comb_type_exon, levels = c("ncRNA","rRNA","yRNA", "protein_coding: exon", "Repeat Element","pseudogene","Antisense Feature","protein_coding: Intron","lncRNA","no Feature")) -->
                                                                                <!-- # p$Same_Comb_type_exon=factor(p$Same_Comb_type_exon, levels = c("ncRNA","rRNA", "protein_coding: exon", "Repeat Element","pseudogene","Antisense Feature","protein_coding: Intron","lncRNA","no Feature")) -->
                                                                                
                                                                                
                                                                                <!-- u=unique(p$Same_Comb_type_exon) -->
                                                                                  <!-- pcount=data.frame(u,1:length(u));colnames(pcount)=c('RNA_Type','Counts_fracMM');  pcount$Counts_Unique=NA   pcount$Counts_MM=NA   pcount$Peak_count=NA -->
                                                                                    <!-- for (x in 1:length(u)) { -->
                                                                                        <!--   pam=p[p$Same_Comb_type_exon%in%u[x],] -->
                                                                                          <!--   pcount[x,1]=u[x] -->
                                                                                            <!--   # pcount[x,'Counts_All']=colSums(pam[,'Allpeaks_Counts_All',drop=F],na.rm = T) -->
                                                                                            <!--   pcount[x,'Counts_Unique']=colSums(pam[,'Allpeaks_Counts_Unique',drop=F],na.rm = T) -->
                                                                                              <!--   pcount[x,'Counts_MM']=colSums(pam[,'Allpeaks_Counts_Multimappers',drop=F],na.rm = T) -->
                                                                                                <!--   # pcount[x,'Counts_primary']=colSums(pam[,'Counts_primary',drop=F],na.rm = T) -->
                                                                                                <!--   pcount[x,'Counts_fracMM']=colSums(pam[,'Allpeaks_Counts_Multimappers_Scaled',drop=F],na.rm = T) -->
                                                                                                  <!--   # pcount[x,'Counts_Primary_fracMM']=colSums(pam[,'Counts_Primary_fracMM',drop=F],na.rm = T) -->
                                                                                                  <!--     pcount[x,'Peak_count']=nrow(pam) -->
                                                                                                    
                                                                                                    <!-- } -->
                                                                                    <!-- pcount$RNA="" -->
                                                                                      
                                                                                      <!-- # gg= -->
                                                                                      <!-- # ggplot(pcount,aes(fill=RNA_Type,x=RNA,y=Counts_All) )+geom_bar(stat='identity',position="stack",width=.5)+theme_classic()+ggtitle("BioType - # of reads (mm+unique) by catagory)")+ -->
                                                                                      <!-- #  scale_fill_brewer(palette = "Dark2")  -->
                                                                                      <!-- # ggplotly(gg) -->
                                                                                      <!-- #  -->
                                                                                      
                                                                                      
                                                                                      <!-- gg= -->
                                                                                        <!-- ggplot(pcount,aes(fill=RNA_Type,x=RNA,y=Counts_fracMM) )+geom_bar(stat='identity',position="stack",width=.5)+theme_classic()+ggtitle("BioType - # of reads (MultiMap scaled) by catagory)")+ -->
                                                                                        <!--  scale_fill_manual(values=nc_color) -->
                                                                                        <!--   # scale_fill_brewer(palette = "Dark2")  -->
                                                                                        
                                                                                        <!-- ggplotly(gg) -->
                                                                                        
                                                                                        
                                                                                        <!-- # if (params$PeakIdnt=='Unique'|params$PeakIdnt=='all'){ -->
                                                                                        
                                                                                        
                                                                                        <!-- #####################################################3 -->
                                                                                        <!-- p=setApeaks_Only -->
                                                                                          <!-- p=p[p$`Allpeaks_Both Strand: RNA_type_Classification`%in%'ncRNA',] -->
                                                                                            <!-- p$Same_Comb_type_exon=p$`Allpeaks_Both Strand: RNA_type_Classification` -->
                                                                                              <!-- p$Same_Comb_type_ncRNA=p$`Allpeaks_Same Strand: ncRNA_Classification` -->
                                                                                                
                                                                                                
                                                                                                <!-- # colnames(p)[colnames(p)%in%'Same_Comb_type_ncRNA']='RNA_Type' -->
                                                                                                <!-- # p$ID_name=paste0(p$ID,"\n",p$Same_gene_name_comb) -->
                                                                                                <!-- #  -->
                                                                                                <!-- #  gg=ggplot(p,aes(x=RNA_Type,y=Allpeaks_Counts_Multimappers_Scaled,fill=RNA_Type) )+geom_violin()+theme_classic()+geom_jitter(height = 0, width = 0.05,size=.5,aes(text=ID_name))+ -->
                                                                                                <!-- #   scale_y_continuous(trans = "log2")+ -->
                                                                                                <!-- #   ggtitle('Peak Counts (Unique + Best Mapped MM) for Ro-Clip\nby ncRNA Type')+ylab("Counts - Ro-Clip")+xlab("")+ -->
                                                                                                <!-- # theme(plot.title = element_text(hjust = 0.5,size = 15),axis.title=element_text(size=15),axis.text=element_text(size=12))+theme(legend.position = "none") + -->
                                                                                                <!-- #     theme(axis.text.x = element_text(angle = -45))+scale_fill_brewer(palette = "Paired") -->
                                                                                                <!-- #  -->
                                                                                                <!-- #  ggplotly(gg,tooltip = c("text", "y")) -->
                                                                                                
                                                                                                <!-- ######################## -->
                                                                                                
                                                                                                <!--  u=unique(p$Same_Comb_type_ncRNA) -->
                                                                                                  <!-- pcount=data.frame(u,1:length(u));colnames(pcount)=c('RNA_Type','Counts_fracMM');  pcount$Counts_Unique=NA   pcount$Counts_MM=NA   pcount$Peak_count=NA -->
                                                                                                    <!-- for (x in 1:length(u)) { -->
                                                                                                        <!--   pam=p[p$Same_Comb_type_ncRNA%in%u[x],] -->
                                                                                                          <!--   pcount[x,1]=u[x] -->
                                                                                                            <!--   # pcount[x,'Counts_All']=colSums(pam[,'Allpeaks_Counts_All',drop=F],na.rm = T) -->
                                                                                                            <!--   pcount[x,'Counts_Unique']=colSums(pam[,'Allpeaks_Counts_Unique',drop=F],na.rm = T) -->
                                                                                                              <!--   pcount[x,'Counts_MM']=colSums(pam[,'Allpeaks_Counts_Multimappers',drop=F],na.rm = T) -->
                                                                                                                <!--   # pcount[x,'Counts_primary']=colSums(pam[,'Counts_primary',drop=F],na.rm = T) -->
                                                                                                                <!--   pcount[x,'Counts_fracMM']=colSums(pam[,'Allpeaks_Counts_Multimappers_Scaled',drop=F],na.rm = T) -->
                                                                                                                  <!--   # pcount[x,'Counts_Primary_fracMM']=colSums(pam[,'Counts_Primary_fracMM',drop=F],na.rm = T) -->
                                                                                                                  <!--     pcount[x,'Peak_count']=nrow(pam) -->
                                                                                                                    
                                                                                                                    <!-- } -->
                                                                                                    <!-- pcount$RNA="" -->
                                                                                                      
                                                                                                      
                                                                                                      <!-- gg= -->
                                                                                                        <!-- ggplot(pcount,aes(fill=RNA_Type,x=RNA,y=Counts_fracMM) )+geom_bar(stat='identity',position="stack",width=.5)+theme_classic()+ggtitle("BioType - # of reads (MultiMap scaled) by catagory)")+ -->
                                                                                                        <!--  scale_fill_manual(values=nc_color) -->
                                                                                                        <!--   # scale_fill_brewer(palette = "Dark2")  -->
                                                                                                        
                                                                                                        <!-- ggplotly(gg) -->
                                                                                                        
                                                                                                        <!-- ``` -->
                                                                                                        
                                                                                                        <!-- <br> -->
                                                                                                        
                                                                                                        
                                                                                                        <!-- <br> -->
                                                                                                        
                                                                                                        <!-- ```{r fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,incude=T} -->
                                                                                                        
                                                                                                        <!-- # Splice_Only -> setApeaks_Only -->
                                                                                                        <!-- ######## -->
                                                                                                        
                                                                                                        <!-- ggplot(setApeaks_Only,aes(x=Allpeaks_Counts_Multimappers_Scaled))+geom_histogram(bins = 15)+ -->
                                                                                                        <!--   scale_x_continuous(trans = "log2") + -->
                                                                                                        <!--   theme_classic()+ylab("# of peaks")+xlab("Peak count")+ggtitle("Number of reads per peaks only Idnetified by \nAllpeaks")+ -->
                                                                                                        <!--   scale_color_brewer(palette = "Dark2") -->
                                                                                                        <!-- # ggplotly(x3,tooltip = c("x", "y","line")) -->
                                                                                                        
                                                                                                        
                                                                                                        <!-- ggplot(setApeaks_Only,aes(x=Allpeaks_Counts_Multimappers_Scaled,line=`Allpeaks_Both Strand: RNA_type_Classification`,color=`Allpeaks_Both Strand: RNA_type_Classification`))+geom_density(size=.5)+ -->
                                                                                                        <!--   scale_x_continuous(trans = "log2") + -->
                                                                                                        <!--   theme_classic()+ylab("Density")+xlab("Peak count")+ggtitle("Number of reads per peaks only Idnetified by \nAllpeaks")+ -->
                                                                                                        <!--   scale_color_brewer(palette = "Dark2") -->
                                                                                                        <!-- # ggplotly(x3,tooltip = c("x", "y","line")) -->
                                                                                                        
                                                                                                        
                                                                                                        <!-- ############################ -->
                                                                                                        <!-- # p=setApeaks_Only -->
                                                                                                        <!-- # p$Allpeaks_Same_Comb_type_exon -->
                                                                                                        <!-- # # if (incd_rRNA==F) { -->
                                                                                                        <!-- # #   p=subset(p,!(Same_Comb_type_ncRNA == 'rRNA')) -->
                                                                                                        <!-- # # } -->
                                                                                                        <!-- # p$Same_Comb_type_exon=as.character(p$Same_Comb_type_exon) -->
                                                                                                        <!-- # p[p$Same_Comb_type_ncRNA%in%'rRNA','Same_Comb_type_exon']='rRNA' -->
                                                                                                        <!-- # p[p$Same_Comb_type_ncRNA%in%'yRNA','Same_Comb_type_exon']='yRNA' -->
                                                                                                        
                                                                                                        <!-- # p$Same_Comb_type_exon=factor(p$Same_Comb_type_exon, levels = c("ncRNA","rRNA","yRNA", "protein_coding: exon", "Repeat Element","pseudogene","Antisense Feature","protein_coding: Intron","lncRNA","no Feature")) -->
                                                                                                        <!-- # p$Same_Comb_type_exon=factor(p$Same_Comb_type_exon, levels = c("ncRNA","rRNA", "protein_coding: exon", "Repeat Element","pseudogene","Antisense Feature","protein_coding: Intron","lncRNA","no Feature")) -->
                                                                                                        
                                                                                                        
                                                                                                        
                                                                                                        
                                                                                                        
                                                                                                        
                                                                                                        <!-- #  -->
                                                                                                        <!-- # ggplot(NoSplice_Only,aes(x=NoSplice_Counts_Unique))+geom_histogram(bins = 15)+ -->
                                                                                                        <!-- #   scale_x_continuous(trans = "log2") + -->
                                                                                                        <!-- #   theme_classic()+ylab("# of peaks")+xlab("Peak count")+ggtitle("Number of reads per peaks only Idnetified by \nNo Splice read Alignemntt")+ -->
                                                                                                        <!-- #   scale_color_brewer(palette = "Dark2") -->
                                                                                                        <!-- # # ggplotly(x3,tooltip = c("x", "y","line")) -->
                                                                                                        <!-- #  -->
                                                                                                        <!-- #  -->
                                                                                                        <!-- # ggplot(NoSplice_Only,aes(x=NoSplice_Counts_Unique,line=`NoSplice_Both Strand: RNA_type_Classification`,color=`NoSplice_Both Strand: RNA_type_Classification`))+geom_density(size=.5)+ -->
                                                                                                        <!-- #   scale_x_continuous(trans = "log2") + -->
                                                                                                        <!-- #   theme_classic()+ylab("Density")+xlab("Peak count")+ggtitle("Number of reads per peaks only Idnetified by \nNo Splice read Alignemnt")+ -->
                                                                                                        <!-- #   scale_color_brewer(palette = "Dark2") -->
                                                                                                        <!-- # # ggplotly(x3,tooltip = c("x", "y","line")) -->
                                                                                                        
                                                                                                        
                                                                                                        <!-- ``` -->
                                                                                                        
                                                                                                        
                                                                                                        
                                                                                                        
                                                                                                        <!-- ```{r ,fig.asp=.5, fig.align='center',fig.height=6, fig.width=12,echo=F,warning=F,eval=F,include=F} -->
                                                                                                        <!-- #RUN2 -->
                                                                                                        <!-- # Peaksdata4=Peaksdata4[,colnames(Peaksdata4)[!colnames(Peaksdata4)%in%c('chr','start','end')]] -->
                                                                                                        <!-- Splice_Peaks$`Peaks Detected in no Splice Alignment`=Splice_Peaks$ID%in%unique(Both_SpliceNoSplice$Splice_ID) -->
                                                                                                          
                                                                                                          <!-- write.table(Splice_Peaks,file=paste0(samplename,"_CLIP_",params$PeakIdnt,"Peaks",ntmerge,'_peakDepth',params$readdepth,params$NameAdd,"_MD15.txt"), sep = "\t", row.names = FALSE, col.names = T, append = F, quote= FALSE,na = "") -->
                                                                                                          <!-- # colnames(Splice_Peaks) -->
                                                                                                          
                                                                                                          <!-- ``` -->